---
title: "Final table"
author: "Beks"
date: "10/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(kableExtra)
```

The code below generates a table on percentages across several key measures. This table was one that was used alongside the lit review to understand the current standing in Zimbabwe, SADC, Africa and the world. This gave some insight into the interactions between MSMEs and the financial sector. The collected data can be compared to other baseline measures. This data is done on the national level so **not** aggregated across provinces.

```{r include=FALSE}
read_complete = read.csv(file = "~/SIVIOgit/clean_FI_2021.csv")
```

```{r}
read_complete %>%
  select(industry, X.2, X.3, X.4, X.5, X.6, X.7, X.8, X.9, X.10, X.11, X.12, X.13, X.14, X.15, X.16, X.17, X.18, X.19, X.20) %>%
  filter(X.20 != "" & (industry != "" | X.2 != "" | X.3 != "" | X.4 != "" | X.5 != "" | X.6 != "" | X.7 != "" | X.8 != "" | X.9 != "" | X.10  != "" | X.11 != "" | X.12 != "" | X.13 != "" | X.14 != "" | X.15 != "" | X.16 != "" | X.17 != "" | X.18 != "" | X.19 != "")) %>%
  pivot_longer(cols = c(industry, X.2, X.3, X.4, X.5, X.6, X.7, X.8, X.9, X.10, X.11, X.12, X.13, X.14, X.15, X.16, X.17, X.18, X.19), names_to = "industry", values_to = "sector") %>%
  filter( sector != "") %>%
  select(-c(industry))

read_complete %>%
  select(funds_start, X.25, X.26, X.27, X.28, X.29, X.30, X.31, X.32, X.33, X.34, X.35, X.36, X.37) %>%
  filter(X.37 != "" & (funds_start != "" | X.25 != "" | X.26 != "" | X.27 != "" | X.28 != "" | X.29 != "" | X.30 != "" | X.31 != "" | X.32 != "" | X.33 != "" | X.34 != "" | X.35 != "" | X.36 != "" )) %>%
  pivot_longer(cols = c(funds_start, X.25, X.26, X.27, X.28, X.29, X.30, X.31, X.32, X.33, X.34, X.35, X.36),
               names_to = "funds", values_to = "start") %>%
  filter(start != "") %>%
  select(-c(funds))

read_complete %>%
  select(funds_ongoing, X.45, X.46, X.47, X.48, X.49, X.50, X.51, X.52, X.53, X.54, X.55, X.56, X.57, X.58) %>%
  filter(X.58 != "" & (funds_ongoing != "" | X.45 != "" | X.46 != "" | X.47 != "" | X.48 != "" | X.49 != "" | X.50 != "" | X.51 != "" | X.52 != "" | X.53 != "" | X.54 != "" | X.55 != "" | X.56 != "" | X.57 != "" )) %>%
  pivot_longer(cols = c(funds_ongoing, X.45, X.46, X.47, X.48, X.49, X.50, X.51, X.52, X.53, X.54, X.55, X.56, X.57), names_to = "funds", values_to = "ongoing") %>%
  filter(ongoing != "") %>%
  select(-c(funds))
```


# clean up data

- pivot longer columns with multiple select
- summarize so as to rename other options
- categorize the other variables
- pivot wider so as to do table analysis break down of each type

```{r}
financial_inclusion_survey = read_complete %>%
  mutate(total_responses = 1) %>%
  
  # business sector/industry
  mutate(industry_not_specified = ifelse(
    (industry == "" & X.2 == "" &  X.3 == "" & X.4 == "" & X.5 == "" & X.6 == "" & X.7 == "" & X.8 == "" & X.9 == "" & X.10 == "" & X.11 == "" & X.12 == "" & X.13 == "" & X.14 == "" & X.15 == "" & X.16 == "" & X.17 == "" & X.18 == "" & X.19 == "" & X.20 == ""), "industry_not_specified", "" ),
    X.20 = trimws(X.20)
    ) %>%
  pivot_longer(cols = c(industry, 
                        X.2, X.3, X.4, X.5, X.6, X.7, X.8, X.9, X.10, X.11, X.12, X.13, X.14, X.15, X.16, X.17, X.18, X.19, X.20, industry_not_specified),
               names_to = "survey_industry",
               values_to = "industry_sector") %>%
  filter(industry_sector != "Other (please specify)",
         industry_sector != "") %>%
  select(-(survey_industry)) %>%
  mutate(single_count = 1) %>%
  pivot_wider(names_from = industry_sector,
              values_from = single_count) %>%
  rename(sector_manufacturing = Manufacturing,
         sector_mining = `Mining and quarrying`,
         sector_vending = `Vending (tuck-shop/flea market)`,
         sector_agriculture = `Agriculture, hunting , forestry and fishing.`,
         sector_retail = `Retail and wholesale`,
         sector_tourism = `Tourism accommodation and Restaurants`,
         sector_professional = `Professional, Consulting, Scientific and Technical Activities`,
         sector_handicrafts = Handicrafts,
         sector_trichology = `Trichology and cosmetology (hair, makeup, nails and beauty therapy)`,
         sector_construction = `Construction Energy, Water and Architecture`,
         sector_logistics = `Logistics and transport`,
         sector_education = Education,
         sector_graphics = `Graphics, Technical design, computer software and Printing`,
         sector_textile = `Textile, apparel, leather`,
         sector_ict = `Information and Communication Technology`,
         sector_catering = `Catering, baking and culinary arts`,
         sector_arts = `Arts, culture, sport, events, media, and entertainment`,
         sector_health = `Health and social services`,
         sector_financial = `Financial services and insurance`,
         ) %>%
  
  # funds to start
  mutate(funds_start_not_specified = ifelse(
    (funds_start == "" & X.25 == "" &  X.26 == "" & X.27 == "" & X.28 == "" & X.29 == "" & X.30 == "" & X.31 == "" & X.32 == "" & X.33 == "" & X.34 == "" & X.35 == "" & X.36 == "" & X.37 == "" ), "funds_start_not_specified", "" ),
    X.20 = trimws(X.37)
    ) %>%
  pivot_longer(cols = c(funds_start, X.25, X.26, X.27, X.28, X.29, X.30, X.31, X.32, X.33, X.34, X.35, X.36, X.37, funds_start_not_specified),
               names_to = "survey_funds_start",
               values_to = "funds_start") %>%
  filter(funds_start != "Other (please specify)",
         funds_start != "") %>%
  select(-(survey_funds_start)) %>%
  mutate(single_count1 = 1) %>%
  pivot_wider(names_from = funds_start,
              values_from = single_count1) %>% 
  rename(start_savings = `Personal savings (from salary or other business initiatives)`,
         start_chimbadzo = `Loan sharks (chimbadzo)`,
         start_familylocal = `Locally based Family and friends`,
         start_banks = Banks,
         start_remittances = `Remittances from family or friends outside Zimbabwe`,
         start_colleagues = `Fellow business colleagues`,
         start_rosals = `Rotating and savings groups`,
         start_localngo = `Local NGOs`,
         start_mfi = `Microfinance institution`,
         start_grant = `International organization through a grant`,
         start_govt = `Government assistance programs`,
         start_creditunion = `Credit unions`,
         start_order_finance = `Order finance companies`) %>%
  
  
  # funds for ongoing business
  # not a required question... so some responses can be blank but a pivot longer will produce multiple blanks so have to group then pivot wider
  # create new variable with not specified so as to keep same filtering as above methods
  mutate(funds_ongoing_not_specified = ifelse(
    (funds_ongoing == "" & X.45 == "" &  X.46 == "" & X.47 == "" & X.48 == "" & X.49 == "" & X.50 == "" & X.51 == "" & X.52 == "" & X.53 == "" & X.54 == "" & X.55 == "" & X.56 == "" & X.57 == "" & X.58 == ""), "funds_ongoing_not_specified", "" ),
    X.58 = trimws(X.58)
    ) %>%
  pivot_longer(cols = c(funds_ongoing, X.45, X.46, X.47, X.48, X.49, X.50, X.51, X.52, X.53, X.54, X.55, X.56, X.57, X.58, funds_ongoing_not_specified),
               names_to = "survey_funds_ongoing",
               values_to = "funds_ongoing") %>%
  filter(funds_ongoing != "Other (please specify)",
         funds_ongoing != ""
         ) %>%
  select(-(survey_funds_ongoing)) %>%
  mutate(count_single = 1) %>%
  pivot_wider(names_from = funds_ongoing,
              values_from = count_single, names_repair = "unique") %>% 
  rename(ongoing_savings = `Personal savings (from salary or other business initiatives)`,
         ongoing_chimbadzo = `Loan sharks (chimbadzo)`,
         ongoing_familylocal = `Locally based family and friends`,
         ongoing_banks = Banks,
         ongoing_remittances = `Remittances from family or friends outside Zimbabwe`,
         ongoing_colleagues = `Fellow business colleagues`,
         ongoing_rosals = `Rotating and Savings Groups`,
         ongoing_localngo = `Local NGOs`,
         ongoing_mfi = `Microfinance institutions`,
         ongoing_grant = `International organization through a grant`,
         ongoing_govt = `Government of Zimbabwe`,
         ongoing_creditunion = `Credit unions`,
         ongoing_orderfinance = `Order finance companies`,
         )
```

# gather entries to rename and then fit into other categories

```{r}
# inclusion_survey %>%
#   group_by(industry_sector) %>%
#   summarise(n=n())
# 
# inclusion_survey %>%
#   group_by(funds_start) %>%
#   summarise(n=n())
# 
# inclusion_survey %>%
#   group_by(funds_ongoing) %>%
#   summarise(n=n())
```

# sum

```{r}
summed_percentages = financial_inclusion_survey %>%
  group_by(province) %>%
  summarise_if(is.numeric, sum, na.rm = TRUE) %>%
  group_by(province) %>%
  summarise(total_responses = total_responses,
            
            # percentage women and men owners
            percent_female_owner = (female_owner/total_responses) * 100,
            percent_male_owner = (male_owner/total_responses) * 100,
            
            # highest level of education of owner
            percent_primary = (primary/total_responses) * 100,
            percent_secondary = (secondary/total_responses) * 100,
            percent_tertiary = (tertiary/total_responses) * 100,
            percent_vocational = (vocational/total_responses) * 100,
            
            # urban rural distribution
            percent_urban = (urban/total_responses) * 100,
            percent_rural = (rural/total_responses) * 100,
            
            # micro small medium distribution
            percent_micro = (micro/total_responses) * 100,
            percent_small = (small/total_responses) * 100,
            percent_medium = (medium/total_responses) * 100,
            
            # sector distribution... same repetitive code... should try to code a loop???
            percent_manufacturing = (sector_manufacturing/total_responses) *100,
            percent_retail = (sector_retail/total_responses) *100,
            percent_agriculture = (sector_agriculture/total_responses) *100,
            percent_mining = (sector_mining/total_responses) *100,
            percent_vending = (sector_vending/total_responses) *100,
            percent_health = (sector_health/total_responses) *100,
            percent_construction = (sector_construction/total_responses) *100,
            percent_education = (sector_education/total_responses) *100,
            percent_catering = (sector_catering/total_responses) *100,
            percent_ict = (sector_ict/total_responses) *100,
            percent_professional = (sector_professional/total_responses) *100,
            percent_arts = (sector_arts/total_responses) *100,
            percent_logistics = (sector_logistics/total_responses) *100,
            percent_financial = (sector_financial/total_responses) *100,
            percent_textile = (sector_textile/total_responses) *100,
            percent_handicrafts = (sector_handicrafts/total_responses) *100,
            percent_tourism = (sector_tourism/total_responses) *100,
            percent_trichology = (sector_trichology/total_responses) *100,
            percent_graphics = (sector_graphics/total_responses) *100,
            
            # access bank
            percent_bank_account = (bank_account_logic/total_responses) *100,
            
            # mobile money
            percent_mobile_account = (mobile_account_logic/total_responses) *100,
            percent_mobile_insurance = (insurance_mobile_awareness_logic/total_responses) *100,
            
            # registration
            percent_registered = (registration_logic/total_responses) * 100,
            percent_zimra = (zimra_register_logic/total_responses) * 100,
            
            # insurance
            percent_insurance = (insurance_logic/total_responses) *100,
            
            # pensions
            percent_pension_policy = (pension_logic/total_responses) *100,
            
            # savings
            percent_saving_facility = (savings_logic/total_responses) *100,
            
            # loans to start up
            percent_savings_start = (start_savings/total_responses) *100,
            percent_chimbadzo_start = (start_chimbadzo/total_responses) *100,
            percent_familylocal_start = (start_familylocal/total_responses) *100,
            percent_banks_start = (start_banks/total_responses) *100,
            percent_remittance_start = (start_remittances/total_responses) *100,
            percent_collegues_start = (start_colleagues/total_responses) *100,
            percent_rosals_start = (start_rosals/total_responses) *100,
            percent_localngo_start = (start_localngo/total_responses) *100,
            percent_mfi_start = (start_mfi/total_responses) *100,
            percent_grant_start = (start_grant/total_responses) *100,
            percent_govt_start = (start_govt/total_responses) *100,
            percent_creditunion_start = (start_creditunion/total_responses) *100,
            
            # loans for ongoing business
            percent_savings_ongoing = (ongoing_savings/total_responses) *100,
            percent_chimbadzo_ongoing = (ongoing_chimbadzo/total_responses) *100,
            percent_familylocal_ongoing = (ongoing_familylocal/total_responses) *100,
            percent_banks_ongoing = (ongoing_banks/total_responses) *100,
            percent_remittance_ongoing = (ongoing_remittances/total_responses) *100,
            percent_collegues_ongoing = (ongoing_colleagues/total_responses) *100,
            percent_rosals_ongoing = (ongoing_rosals/total_responses) *100,
            percent_localngo_ongoing = (ongoing_localngo/total_responses) *100,
            percent_mfi_ongoing = (ongoing_mfi/total_responses) *100,
            percent_grant_ongoing = (ongoing_mfi/total_responses) *100,
            percent_govt_ongoing = (ongoing_govt/total_responses) *100,
            percent_creditunion_ongoing = (ongoing_creditunion/total_responses) *100,
            percent_orderfinance_ongoing = (ongoing_orderfinance/total_responses) *100,
            
            ) %>%
  mutate_if(is.numeric, round, 2)

summed_percentages
```

# Averages

```{r}
averages = financial_inclusion_survey %>%
  group_by(province) %>%
  summarise(# average size of business by number of employees
            average_num_employees = mean(num_employees, na.rm = T),
            
            # average size of business by revenue
            average_annual_turnover = mean(annual_turnover, na.rm = T),
            
            # average size of business by assets
            average_gross_assets = mean(gross_assets, na.rm = T),
  ) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(enterprise_category = ifelse(average_num_employees <= 5 & 
                               average_gross_assets <= 10000 & 
                               average_annual_turnover <= 30000, 
                             "micro", 
                             ifelse(average_num_employees <= 30 & average_num_employees > 5 &
                                      average_gross_assets <= 250000 & average_gross_assets > 30000 &
                                      average_annual_turnover <= 50000 & average_annual_turnover > 30000, 
                                    "small",
                                    ifelse(average_num_employees <= 75 & average_num_employees > 30 &
                                             average_gross_assets <= 500000 & average_gross_assets > 250000 &
                                             average_annual_turnover <= 500000 & average_annual_turnover > 50000, 
                                           "medium",
                                           "other"))),
         points = 0,
         points = case_when(
           average_num_employees < 5 ~ points+1,
           average_num_employees < 30 ~ points+2,
           average_num_employees < 75 ~ points+3,
           TRUE ~ points+4
         ),
         points = case_when(
           average_gross_assets < 10000 ~ points+1,
           average_gross_assets < 250000 ~ points+2,
           average_gross_assets < 500000 ~ points+3,
           TRUE ~ points+4
         ),
         points = case_when(
           average_annual_turnover < 30000 ~ points+1,
           average_annual_turnover < 50000 ~ points+2,
           average_annual_turnover < 1000000 ~ points+3,
           TRUE ~ points+4
         )) %>%
  mutate(enterprise_category = ifelse(enterprise_category == "other" & points <= 4, "micro",
                             ifelse(enterprise_category == "other" & points <= 7 & points >= 5, "small",
                                    ifelse(enterprise_category == "other" & points <= 9 & points >= 8, "medium", enterprise_category)))
         )
averages
```

# Day to open

```{r}
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
```

```{r}
days = financial_inclusion_survey %>%
  filter(time_open_bank_account != "",
         time_open_mobile_money_account != "") %>%
  group_by(province) %>%
  summarise(mode_days_open_bank = getmode(time_open_bank_account),
            mode_days_open_mobile = getmode(time_open_mobile_money_account))
days
```

# Select Variables

```{r}
final_table = summed_percentages %>%
  left_join(averages, by = "province") %>%
  left_join(days, by = "province") %>%
  select(province,
         total_responses,
         
         percent_female_owner, percent_male_owner,
         
         percent_primary, percent_secondary, percent_tertiary, percent_vocational,
         
         average_num_employees,
         average_annual_turnover,
         average_gross_assets,
         enterprise_category,
         
         percent_rural, percent_urban,
         
         percent_micro, percent_small, percent_medium,
         
         percent_manufacturing, percent_retail, percent_agriculture, percent_mining,
         percent_vending, percent_health, percent_construction, percent_education,
         percent_catering, percent_ict, percent_professional, percent_arts,
         percent_logistics, percent_financial, percent_textile, percent_handicrafts,
         percent_tourism, percent_trichology, percent_graphics,
         
         percent_bank_account,
         mode_days_open_bank,
         
         percent_mobile_account,
         mode_days_open_mobile,
         percent_mobile_insurance,
         
         percent_registered,
         percent_zimra,
         
         percent_insurance,
         percent_pension_policy,
         percent_saving_facility,
         
         
         percent_savings_start, percent_chimbadzo_start, percent_familylocal_start,
         percent_banks_start, percent_remittance_start, percent_collegues_start,
         percent_rosals_start, percent_localngo_start, percent_mfi_start,
         percent_grant_start, percent_govt_start, percent_creditunion_start,
         
         percent_savings_ongoing, percent_chimbadzo_ongoing, percent_familylocal_ongoing,
         percent_banks_ongoing, percent_remittance_ongoing, percent_collegues_ongoing,
         percent_rosals_ongoing, percent_localngo_ongoing, percent_mfi_ongoing,
         percent_grant_ongoing, percent_govt_ongoing, percent_creditunion_ongoing,
         percent_orderfinance_ongoing,
         )
```

```{r}
write.csv(final_table, file = "~/SIVIOgit/province_summary_2021.csv")
```

```{r}
final_table %>%
  kable() %>%
  kable_styling()
```

