---
title: "availability"
author: "Beks"
date: "10/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(kableExtra)
```

```{r}
data = read.csv(file = "~/SIVIOgit/clean_FI_2021.csv")
# data = read.csv(file = "~/SIVIOgit/data_equal_comparisons.csv")
```

# levels of inclusion.

This can be used to compare across the different measures.

```{r}
# "province",
# "gender_inclusion", 
# "location_inclusion", 
# "size_inclusion",
# "age_inclusion",
# "formality_inclusion",
# "sector_inclusion"

level = c("province")
```

## Criteria

```{r include=FALSE}
criteria = c(
  "bank_account_value",
  "time_open_bank_value",
  "sme_auction_value",
  
  # "time_approval_commercial_value",
  # "collateral_commercial_value",
  # "other_financial_value",
  # "time_approval_other_value",
  # "collateral_other_value",
  # "insurance_value",
  
  "pension_value",
  "mm_account_value",
  "time_open_mm_value",
  "insurance_mm_value",
  "savings_facility_value",
  "advice_sources_value")

ncriteria = length(criteria)

```

There are `r ncriteria` criteria

The criteria are `r criteria`


## Banking

### Bank account

```{r echo=FALSE}
bank_account = data %>%
  select(all_of(level),
         bank_account, bank_account_logic) %>%
  mutate(not_answered = ifelse(bank_account == "", 1, 0)) %>%
  group_by(across(all_of(level))) %>%
  summarise(not_answered_bank_account = sum(not_answered, na.rm = T),
            bank_account = sum(bank_account_logic, na.rm = T),
            responses = n()) %>%
  mutate(bank_account_value = bank_account / (responses - not_answered_bank_account)) 


bank_account %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

### Time open bank account

- time_open_bank_account == "1 day /same day service" ~ 5,

- time_open_bank_account == "2 to 3 days" ~ 5,

- time_open_bank_account == "4 to 6 days" ~ 4,

- time_open_bank_account == "7 to 10 days" ~ 3,

- time_open_bank_account == "11 to 30 days" ~ 2,

- time_open_bank_account == "31 days plus" ~ 1

Final value is calculated as the average score and then divided by 5 so as to normalize between 0-1

When displayed, it will be rounded off so as to use categories so a 4.5 = "< 3 days" a 3.2 = "7 to 10 days"

```{r echo=FALSE}
time_open_bank = data %>%
  select(all_of(level),
         bank_account, time_open_bank_account) %>%
  filter(bank_account == "Yes") %>%
  mutate(time_open = case_when(
    time_open_bank_account == "1 day /same day service" ~ 5,
    time_open_bank_account == "2 to 3 days" ~ 5,
    time_open_bank_account == "4 to 6 days" ~ 4,
    time_open_bank_account == "7 to 10 days" ~ 3,
    time_open_bank_account == "11 to 30 days" ~ 2,
    time_open_bank_account == "31 days plus" ~ 1,
    TRUE ~ as.double(0)
  )) %>%
  filter(time_open != 0) %>%
  group_by(across(all_of(level))) %>%
  summarise(resposnes = n(),
            time_open_value = mean(time_open)) %>%
  mutate(time_open_bank_value = time_open_value / 5) 

time_open_bank %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

### SME auction

- those who need foreign currency, are they registered on the SME foreign exchange auction

```{r echo=FALSE}
sme_auction = data %>%
  select(all_of(level), 
          sme_foreign_exchange_auction,sme_auction_logic, foreign_currency, foreign_currency_logic) %>%
  filter(foreign_currency == "Yes") %>%
  mutate(not_answered = ifelse(sme_foreign_exchange_auction == "", 1, 0)) %>%
  group_by(across(all_of(level))) %>%
  summarise(sme_foreign_exchange_auction = sum(sme_auction_logic, na.rm = T),
            responses = n(),
            not_answered_sme = sum(not_answered, na.rm = T)) %>%
  mutate(sme_auction_value = sme_foreign_exchange_auction / (responses - not_answered_sme)) 

sme_auction %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

## Commercial Loans

### approval time

- time_approval_commercial_loan == "1 day /same day service" ~ 5,

- time_approval_commercial_loan == "2 to 3 days" ~ 5,

- time_approval_commercial_loan == "4 to 6 days" ~ 5,

- time_approval_commercial_loan == "7 to 10 days" ~ 4,

- time_approval_commercial_loan == "11 to 30 days" ~ 3,

- time_approval_commercial_loan == "31 to 60 days" ~ 2,

- time_approval_commercial_loan == "60 to 90 days" ~ 2,

- time_approval_commercial_loan == "91 days plus" ~ 1

This is calculated for 12 months, then again for the previous four years. Then averaged across the 2 groups so as to find the average for the last five years

The final value is the average of the scores then divided by 5 to normalize between 0 and 1

The final displayed score will be rounded off so as to land in a category

```{r echo=FALSE}
# 12 months
time_12months = data %>%
  select(all_of(level), 
         commercial_loan_application,
         number_commercial_loan_applications_12months, time_approval_commercial_loan_12months) %>%
  filter(commercial_loan_application == "Yes") %>%
  filter(number_commercial_loan_applications_12months != "Never" & 
           number_commercial_loan_applications_12months != "") %>%
  mutate(not_answered = ifelse(time_approval_commercial_loan_12months == "", 1, 0),
         time_approval = case_when(
           time_approval_commercial_loan_12months == "1 day /same day service" ~ 5,
           time_approval_commercial_loan_12months == "2 to 3 days" ~ 5,
           time_approval_commercial_loan_12months == "4 to 6 days" ~ 5,
           time_approval_commercial_loan_12months == "7 to 10 days" ~ 4,
           time_approval_commercial_loan_12months == "11 to 30 days" ~ 3,
           time_approval_commercial_loan_12months == "31 to 60 days" ~ 2,
           time_approval_commercial_loan_12months == "60 to 90 days" ~ 2,
           time_approval_commercial_loan_12months == "91 days plus" ~ 1, 
           TRUE ~ as.double(0)
         ))%>%
  filter(time_approval != 0) %>%
  group_by(across(all_of(level))) %>%
  summarise(time_approval_12months_full = mean(time_approval, na.rm = T),
              not_answered_time_12months = sum(not_answered, na.rm = T),
            responses_time_12months = n()) %>%
  mutate(time_approval_12months = time_approval_12months_full / 5)

# 4 years
time_4years = data %>%
  select(all_of(level), 
         commercial_loan_application,
         number_commercial_loan_applications_4years, time_approval_commercial_loan_4years) %>%
  filter(commercial_loan_application == "Yes") %>%
  filter(number_commercial_loan_applications_4years != "Never" & 
           number_commercial_loan_applications_4years != "") %>%
  mutate(not_answered = ifelse(time_approval_commercial_loan_4years == "", 1, 0),
         time_approval = case_when(
           time_approval_commercial_loan_4years == "1 day /same day service" ~ 5,
           time_approval_commercial_loan_4years == "2 to 3 days" ~ 5,
           time_approval_commercial_loan_4years == "4 to 6 days" ~ 5,
           time_approval_commercial_loan_4years == "7 to 10 days" ~ 4,
           time_approval_commercial_loan_4years == "11 to 30 days" ~ 3,
           time_approval_commercial_loan_4years == "31 to 60 days" ~ 2,
           time_approval_commercial_loan_4years == "60 to 90 days" ~ 2,
           time_approval_commercial_loan_4years == "91 days plus" ~ 1, 
           TRUE ~ as.double(0)
         ))%>%
  filter(time_approval != 0) %>%
  group_by(across(all_of(level))) %>%
  summarise(time_approval_4years_full = mean(time_approval),
            not_answered_time_4years = sum(not_answered),
            responses_time_4years = n()) %>%
  mutate(time_approval_4years = time_approval_4years_full / 5)

# combine
time_approval_commercial = time_12months %>%
  full_join((time_4years), by = (all_of(level)))

time_approval_commercial$time_approval_commercial_value = rowMeans(time_approval_commercial[, c( "time_approval_12months" , "time_approval_4years" )])

time_approval_commercial %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

### Collateral

for those who applied for a loan in the last five years, did they need collateral. "Yes" = 0, "No" = 1 ...

```{r echo=FALSE}
# 12 months
collateral_12months = data %>%
  select(all_of(level),
         commercial_loan_application, number_commercial_loan_applications_12months,
         collateral_commercial_loan_12months, collateral_commercial_loan_12months_logic) %>%
  filter(commercial_loan_application == "Yes") %>%
  filter(number_commercial_loan_applications_12months != "" & number_commercial_loan_applications_12months != "Never") %>%
  mutate(not_answered = ifelse(collateral_commercial_loan_12months == "", 1, 0)) %>%
  group_by(across(all_of(level))) %>%
  summarise(collateral_commercial_loan_12months = sum(collateral_commercial_loan_12months_logic, na.rm = T),
            not_answered_collateral_12months = sum(not_answered),
            responses_collateral_12months = n()) %>%
  mutate(collateral_commercial_loan_12months = collateral_commercial_loan_12months / (responses_collateral_12months - not_answered_collateral_12months))

# 4 years
collateral_4years = data %>%
  select(all_of(level), 
         commercial_loan_application, number_commercial_loan_applications_4years,
         collateral_commercial_loan_4years, collateral_commercial_loan_4years_logic) %>%
  filter(commercial_loan_application == "Yes") %>%
  filter(number_commercial_loan_applications_4years != "" & number_commercial_loan_applications_4years != "Never") %>%
  mutate(not_answered = ifelse(collateral_commercial_loan_4years == "", 1, 0)) %>%
  group_by(across(all_of(level))) %>%
  summarise(collateral_commercial_loan_4years = sum(collateral_commercial_loan_4years_logic, na.rm = T),
            not_answered_collateral_4years = sum(not_answered),
            responses_collateral_4years = n()) %>%
  mutate(collateral_commercial_loan_4years = collateral_commercial_loan_4years / (responses_collateral_4years - not_answered_collateral_4years))

# combine
collateral_commercial = collateral_12months %>%
  full_join((collateral_4years), by = (all_of(level)))

collateral_commercial$collateral_commercial_value = rowMeans(collateral_commercial[, c("collateral_commercial_loan_12months", "collateral_commercial_loan_4years")], na.rm = T)

collateral_commercial %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

## other financial services

### Relationship with other financial services

Those who have a relationship with a another financial service

```{r echo=FALSE}
other_financial = data %>%
  select(all_of(level),
         other_finance_institutions, other_finance_institutions_logic) %>%
  mutate(not_answered = ifelse(other_finance_institutions == "", 1, 0)) %>%
  group_by(across(all_of(level))) %>%
  summarise(other_finance_institutions = sum(other_finance_institutions_logic),
            responses = n(),
            not_answered_other_financial = sum(not_answered)) %>%
  mutate(other_financial_value = other_finance_institutions / (responses - not_answered_other_financial)) 

other_financial %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

### time approval for loan over last 5 years

- time_approval_loan == "1 day /same day service" ~ 5,

- time_approval_loan == "2 to 3 days" ~ 5,

- time_approval_loan == "4 to 6 days" ~ 5,

- time_approval_loan == "7 to 10 days" ~ 4,

- time_approval_loan == "11 to 30 days" ~ 3,

- time_approval_loan == "31 to 60 days" ~ 2,

- time_approval_loan == "60 to 90 days" ~ 2,

- time_approval_loan == "91 days plus" ~ 1

Averaged for 12 months and previous 4 years

```{r echo=FALSE}
time_approval_other = data %>%
  select(all_of(level), 
         time_approval_loan_other_5years,
         loan_other_5years, X.97, X.98, X.99, X.100, X.101, X.102, X.103, X.104, X.105, X.106, X.107, X.108) %>%
  filter(X.108 == "") %>% # none of the above
  mutate(formal_loan_other = case_when(
           loan_other_5years != "" ~ 1, # micro finance
           X.97 != "" ~ 1, # order finance companies
           X.98 != "" ~ 1, # Money clubs 
           X.100 != "" ~ 1, # credit unions
           X.101 != "" ~ 1, # fellow business colleagues
           X.102 != "" ~ 1, # local ngo
           X.103 != "" ~ 1, # government of Zimbabwe
           X.104 != "" ~ 1, # international org through grant
           X.107 != "" ~ 1, # fellow business colleagues
           TRUE ~ as.double(0)),
         informal_loan_other = case_when(
           X.99 != "" ~ 1, # loan sharks
           X.105 != "" ~ 1, # local family/friends
           X.106 != "" ~ 1, # remittances
           TRUE ~ as.double(0)),
         other_loan_source = case_when(
           informal_loan_other == 1 & formal_loan_other == 0 ~ "informal",
           formal_loan_other == 1 & informal_loan_other == 0 ~ "fomal",
           informal_loan_other == 1 & formal_loan_other == 1 ~ "both",
           TRUE ~ as.character("not answered")
           ),
         not_answered = ifelse(formal_loan_other == 0 & informal_loan_other == 0, 1, 0),
         time_approval = case_when(
           time_approval_loan_other_5years == "1 day /same day service" ~ 5,
           time_approval_loan_other_5years == "2 to 3 days" ~ 5,
           time_approval_loan_other_5years == "4 to 6 days" ~ 5,
           time_approval_loan_other_5years == "7 to 10 days" ~ 4,
           time_approval_loan_other_5years == "11 to 30 days" ~ 3,
           time_approval_loan_other_5years == "31 to 60 days" ~ 2,
           time_approval_loan_other_5years == "60 to 90 days" ~ 2,
           time_approval_loan_other_5years == "91 days plus" ~ 1, 
           TRUE ~ as.double(0))
         ) %>%
  filter(not_answered == 0) %>%
  filter(time_approval != 0) %>%
  group_by(across(all_of(level))) %>%
  summarise(time_approval_loan_other_5years = mean(time_approval),
            not_answered_time_other = sum(not_answered),
            responses = n()) %>%
  mutate(time_approval_other_value = time_approval_loan_other_5years / 5) 

time_approval_other %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

#### Formal, informal sources

Formal sources of loans

- micro finance institution

- order finance

- money clubs

- credit unions

- fellow business colleagues

- local NGO

- government of Zimbabwe

- international grant

Informal sources

- loan sharks

- local family/friends

- remittances

```{r echo=FALSE}
# data %>%
#   select(all_of(level),
#          time_approval_loan_other_5years,
#          loan_other_5years, X.97, X.98, X.99, X.100, X.101, X.102, X.103, X.104, X.105, X.106, X.107, X.108) %>%
#   filter(X.108 == "") %>% # none of the above
#   mutate(formal_loan_other = case_when(
#            loan_other_5years != "" ~ 1, # micro finance
#            X.97 != "" ~ 1, # order finance companies
#            X.98 != "" ~ 1, # Money clubs 
#            X.100 != "" ~ 1, # credit unions
#            X.101 != "" ~ 1, # fellow business colleagues
#            X.102 != "" ~ 1, # local ngo
#            X.103 != "" ~ 1, # government of Zimbabwe
#            X.104 != "" ~ 1, # international org through grant
#            X.107 != "" ~ 1, # fellow business colleagues
#            TRUE ~ as.double(0)),
#          informal_loan_other = case_when(
#            X.99 != "" ~ 1, # loan sharks
#            X.105 != "" ~ 1, # local family/friends
#            X.106 != "" ~ 1, # remittances
#            TRUE ~ as.double(0)),
#          other_loan_source = case_when(
#            informal_loan_other == 1 & formal_loan_other == 0 ~ "informal",
#            formal_loan_other == 1 & informal_loan_other == 0 ~ "fomal",
#            informal_loan_other == 1 & formal_loan_other == 1 ~ "both",
#            TRUE ~ as.character("not answered")
#            ),
#          not_answered = ifelse(formal_loan_other == 0 & informal_loan_other == 0, 1, 0),
#          time_approval = case_when(
#            time_approval_loan_other_5years == "1 day /same day service" ~ 5,
#            time_approval_loan_other_5years == "2 to 3 days" ~ 5,
#            time_approval_loan_other_5years == "4 to 6 days" ~ 5,
#            time_approval_loan_other_5years == "7 to 10 days" ~ 4,
#            time_approval_loan_other_5years == "11 to 30 days" ~ 3,
#            time_approval_loan_other_5years == "31 to 60 days" ~ 2,
#            time_approval_loan_other_5years == "60 to 90 days" ~ 2,
#            time_approval_loan_other_5years == "91 days plus" ~ 1, 
#            TRUE ~ as.double(0))
#          ) %>%
#   filter(not_answered == 0) %>%
#   filter(time_approval != 0) %>%
#   group_by(across(all_of(level)), other_loan_source) %>%
#   summarise(time_approval_loan_other_5years = mean(time_approval),
#             not_answered_time_other = sum(not_answered),
#             responses = n()) %>%
#   mutate(time_approval_loan_other_5years = time_approval_loan_other_5years/5) %>%
#   kable() %>%
#   kable_styling()
```


### collateral

For those who got a loan from at least one formal financial institution, did they provide collateral... 1 if no

Filter out those who got from an informal source

```{r echo=FALSE}
collateral_other = data %>%
  select(all_of(level),
         collateral_loan_other_5years, collateral_loan_other_5years_logic,
         loan_other_5years, X.97, X.98, X.99, X.100, X.101, X.102, X.103, X.104, X.105, X.106, X.107, X.108) %>%
  filter(X.108 == "") %>% # none of the above
  mutate(formal_loan_other = case_when(
           loan_other_5years != "" ~ 1, # micro finance
           X.97 != "" ~ 1, # order finance companies
           X.98 != "" ~ 1, # Money clubs 
           X.100 != "" ~ 1, # credit unions
           X.101 != "" ~ 1, # fellow business colleagues
           X.102 != "" ~ 1, # local ngo
           X.103 != "" ~ 1, # government of Zimbabwe
           X.104 != "" ~ 1, # international org through grant
           X.107 != "" ~ 1, # fellow business colleagues
           TRUE ~ as.double(0)),
         informal_loan_other = case_when(
           X.99 != "" ~ 1, # loan sharks
           X.105 != "" ~ 1, # local family/friends
           X.106 != "" ~ 1, # remittances
           TRUE ~ as.double(0)),
         other_loan_source = case_when(
           informal_loan_other == 1 & formal_loan_other == 0 ~ "informal",
           formal_loan_other == 1 & informal_loan_other == 0 ~ "fomal",
           informal_loan_other == 1 & formal_loan_other == 1 ~ "formal",
           TRUE ~ as.character("not answered")
           ),
         not_answered_loan = ifelse(formal_loan_other == 0 & informal_loan_other == 0, 1, 0),
         not_answered = ifelse(collateral_loan_other_5years == "", 1, 0)
  ) %>%
  filter(other_loan_source == "informal") %>%
  group_by(across(all_of(level))) %>%
  summarise(collateral_loan_other_5years = sum(collateral_loan_other_5years_logic),
            responses = n(),
            not_answered_collateral = sum(not_answered)) %>%
  mutate(collateral_other_value = collateral_loan_other_5years / (responses - not_answered_collateral)) 

collateral_other %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()

```

## Insurance

Those who have insurance business producs

```{r echo=FALSE}
insurance = data %>%
  select(all_of(level),
         insurance_business_products, insurance_logic) %>%
  mutate(not_answered = ifelse(insurance_business_products == "", 1, 0)) %>%
  group_by(across(all_of(level))) %>%
  summarise(has_insurance = sum(insurance_logic),
            responses = n(),
            not_answered_insurance = sum(not_answered)) %>%
  mutate(insurance_value = has_insurance / (responses - not_answered_insurance)) 

insurance %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

## Pensions

Businesses that have a pension policy

```{r echo=FALSE}
pension = data %>%
  select(all_of(level),
         pension_policy, pension_logic) %>%
  mutate(not_answered = ifelse(pension_policy == "", 1, 0)) %>%
  group_by(across(all_of(level))) %>%
  summarise(has_pension_policy = sum(pension_logic),
            responses = n(),
            not_answered_pension = sum(not_answered)) %>%
  mutate(pension_value = has_pension_policy / (responses - not_answered_pension)) 

pension %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

## Mobile Money
         
### account

Those that have a MM for their business

```{r echo=FALSE}
mm_account = data %>%
  select(all_of(level),
         mobile_money_account, mobile_account_logic) %>%
  mutate(not_answered = ifelse(mobile_money_account == "", 1, 0)) %>%
  group_by(across(all_of(level))) %>%
  summarise(mobile_money_account = sum(mobile_account_logic),
            responses = n(),
            not_answered_mobile_account = sum(not_answered)) %>%
  mutate(mm_account_value = mobile_money_account / (responses - not_answered_mobile_account)) 

mm_account %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

### time open account

- time_open_mobile_money_account == "1 day /same day service" ~ 5,

- time_open_mobile_money_account == "2 to 3 days" ~ 5,

- time_open_mobile_money_account == "4 to 6 days" ~ 4,

- time_open_mobile_money_account == "7 to 10 days" ~ 3,

- time_open_mobile_money_account == "11 to 30 days" ~ 2,

- time_open_mobile_money_account == "31 days plus" ~ 1,

```{r echo=FALSE}
time_open_mm = data %>%
  select(all_of(level), 
         mobile_money_account, time_open_mobile_money_account) %>%
  filter(mobile_money_account == "Yes") %>%
  mutate(time_open = case_when(
    time_open_mobile_money_account == "1 day /same day service" ~ 5,
    time_open_mobile_money_account == "2 to 3 days" ~ 5,
    time_open_mobile_money_account == "4 to 6 days" ~ 4,
    time_open_mobile_money_account == "7 to 10 days" ~ 3,
    time_open_mobile_money_account == "11 to 30 days" ~ 2,
    time_open_mobile_money_account == "31 days plus" ~ 1,
    TRUE ~ as.double(0)
  )) %>%
  filter(time_open != 0) %>%
  group_by(across(all_of(level))) %>%
  summarise(resposnes = n(),
            time_open_mm_value = mean(time_open) / 5) 

time_open_mm %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

### insuracnce awareness

Proportion aware of insurance products offered on mobile money account... for those who have a mobile money account

```{r echo=FALSE}
insurance_mm = data %>%
  select(all_of(level),
         mobile_money_account, insurance_mobile_awareness, insurance_mobile_awareness_logic) %>%
  filter(mobile_money_account == "Yes") %>%
  mutate(not_answered = ifelse(insurance_mobile_awareness == "", 1, 0)) %>%
  group_by(across(all_of(level))) %>%
  summarise(insurance_mobile_awareness = sum(insurance_mobile_awareness_logic),
            responses = n(),
            not_answered_mobile_insurance_aware = sum(not_answered)) %>%
  mutate(insurance_mm_value = insurance_mobile_awareness / (responses - not_answered_mobile_insurance_aware)) 

insurance_mm %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```


## Investments and Capital Markets

Have access to a savings facility

```{r echo=FALSE}
savings_facility = data %>%
  select(all_of(level),
         savings_facility_access, savings_logic) %>%
  mutate(not_answered = ifelse(savings_facility_access == "", 1, 0)) %>%
  group_by(across(all_of(level))) %>%
  summarise(access_savings_facility = sum(savings_logic),
            responses = n(),
            not_answered_savings = sum(not_answered)) %>%
  mutate(savings_facility_value = access_savings_facility / (responses - not_answered_savings)) 

savings_facility %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

## Access to Information

Business advice

- Formal sources (bank, accountant, financial advisor, investment broker) 

- Informal & informal sources

- Informal sources (family, friends)

```{r echo=FALSE}
advice_sources = data %>%
  select(all_of(level),
         business_advice) %>%
  mutate(business_advice_logic = case_when(
    business_advice == "Formal sources (bank, accountant, financial advisor, investment broker)"~ 1,
    business_advice == "Informal & informal sources" ~ 1,
    business_advice == "Informal sources (family, friends)" ~ 0,
    TRUE ~ as.double(0)),
    not_answered = ifelse(business_advice == "", 1, 0)
    ) %>%
  group_by(across(all_of(level))) %>%
  summarise(business_advice = sum(business_advice_logic),
            responses = n(),
            not_answered_advice = sum(not_answered)) %>%
  mutate(advice_sources_value = business_advice / (responses - not_answered_advice))

advice_sources %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

## Final Table

```{r echo=FALSE}
availability_critera = data %>%
  group_by(across(all_of(level))) %>%
  summarise(n=n()) %>%
  full_join(y = (bank_account %>% select(all_of(level), bank_account_value)), by = all_of(level)) %>%
  full_join(y = (time_open_bank %>% select(all_of(level), time_open_bank_value)), by = all_of(level)) %>%
  full_join(y = (sme_auction %>% select(all_of(level), sme_auction_value)), by = all_of(level)) %>%
  full_join(y = (time_approval_commercial %>% select(all_of(level), time_approval_commercial_value)), by = all_of(level)) %>%
  full_join(y = (collateral_commercial %>% select(all_of(level), collateral_commercial_value)), by = all_of(level)) %>%
  full_join(y = (other_financial %>% select(all_of(level), other_financial_value)), by = all_of(level)) %>%
  full_join(y = (time_approval_other %>% select(all_of(level), time_approval_other_value)), by = all_of(level)) %>%
  full_join(y = (collateral_other %>% select(all_of(level), collateral_other_value)), by = all_of(level)) %>%
  full_join(y = (insurance %>% select(all_of(level), insurance_value)), by = all_of(level)) %>%
  full_join(y = (pension %>% select(all_of(level), pension_value)), by = all_of(level)) %>%
  full_join(y = (mm_account %>% select(all_of(level), mm_account_value)), by = all_of(level)) %>%
  full_join(y = (time_open_mm %>% select(all_of(level), time_open_mm_value)), by = all_of(level)) %>%
  full_join(y = (insurance_mm %>% select(all_of(level), insurance_mm_value)), by = all_of(level)) %>%
  full_join(y = (savings_facility %>% select(all_of(level), savings_facility_value)), by = all_of(level)) %>%
  full_join(y = (advice_sources %>% select(all_of(level), advice_sources_value)), by = all_of(level)) %>%
  mutate_if(is.numeric, replace_na, 0.5)

availability_critera$availability_score = rowSums(availability_critera[, c(
  all_of(criteria))])

availability_critera$availability_normalise = (availability_critera$availability_score / ncriteria)

availability_critera$availability_percentage = round((availability_critera$availability_normalise * 100),2)

availability_critera %>%
  kable() %>%
  kable_styling()
```

```{r}
write.csv(availability_critera, file = "~/SIVIOgit/availability_criteria.csv")
```

