---
title: "barriers"
author: "Beks"
date: "10/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(kableExtra)
```

```{r}
data = read.csv(file = "~/SIVIOgit/clean_financial_inclusion.csv")
```

# levels of inclusion.

This can be used to compare across the different measures.

```{r}
# province
# gender_inclusion 
# location_inclusion 
# size_inclusion
# age_inclusion
# formality_inclusion
# sector_inclusion

level = c("province")
```

```{r}
provincial_totals = c(128,155,151,111,125,161,154,144,134,125)
```


# Penetration Barriers

## Business characteristics

## Registration 

- not registered

- not registered with Zimra

### Knowledge, Finance/Affordability, Complicated law, Bureaucracy

```{r echo=FALSE}
register = data %>%
  select(all_of(level), 
         registered, reason_not_registered) %>%
  filter(registered == "No") %>%
  # filter(reason_not_registered != "I simply do not want to register.") %>%
  mutate(not_answered = ifelse(reason_not_registered == "", 1, 0),
         knowledge = ifelse(reason_not_registered == "I do not know how to register.", 1, 0),
         finance = ifelse(reason_not_registered == "It costs too much", 1, 0),
         law = ifelse(reason_not_registered == "Lack of simplicity and accuracy of the company registration law", 1, 0),
         bureaucracy = ifelse(reason_not_registered == "The process is bureaucratic.", 1, 0)
         ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            finance = sum(finance),
            law = sum(law),
            bureaucracy = sum(bureaucracy),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_register = knowledge / (responses - not_answered_reason),
         finance_register = finance / (responses - not_answered_reason),
         law_register = law / (responses - not_answered_reason),
         bureaucracy_register = bureaucracy / (responses - not_answered_reason))

register %>%
  kable() %>%
  kable_styling()
```

```{r echo=FALSE}
zimra = data %>%
  select(all_of(level), 
         zimra_registration, reason_not_zimra) %>%
  filter(zimra_registration == "None of the above")%>%
  # filter(reason_not_zimra != "I don’t need any of the above to operate") %>%
  mutate(not_answered = ifelse(reason_not_zimra == "", 1, 0),
         knowledge = ifelse(reason_not_zimra == "I do not know how to register.", 1, 0),
         finance = ifelse(reason_not_zimra == "Taxes are too high.", 1, 0),
         inflation = ifelse(reason_not_zimra == "Inflation", 1, 0),
         law = ifelse(reason_not_zimra == "Lack of simplicity and accuracy of the tax legislation", 1, 0),
         bureaucracy = ifelse(reason_not_zimra == "The process is bureaucratic.", 1, 0)
         ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            finance = sum(finance),
            inflation = sum(inflation),
            law = sum(law),
            bureaucracy = sum(bureaucracy),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_zimra = knowledge / (responses - not_answered_reason),
         finance_zimra = finance / (responses - not_answered_reason),
         inflation_zimra = inflation / (responses - not_answered_reason),
         law_zimra = law / (responses - not_answered_reason),
         bureaucracy_zimra = bureaucracy / (responses - not_answered_reason),
         
         knowledge_zimra = ifelse(responses == not_answered_reason, 0 , knowledge_zimra),
         finance_zimra = ifelse(responses == not_answered_reason, 0 , finance_zimra),
         inflation_zimra = ifelse(responses == not_answered_reason, 0 , inflation_zimra),
         law_zimra = ifelse(responses == not_answered_reason, 0 , law_zimra),
         bureaucracy_zimra = ifelse(responses == not_answered_reason, 0 , bureaucracy_zimra),
         )

zimra %>%
  kable() %>%
  kable_styling()
```


## Banking

- reason no bank account

### Documentation, legal standing, finance, trust, bureaucracy

- reason not registered on SME auction

### Knowledge, legal standing, finance, Complicated law, trust

```{r echo=FALSE}
bank_account = data %>%
  select(all_of(level), 
         bank_account, reason_no_bank_account) %>%
  filter(bank_account == "No") %>%
  # filter(reason_no_bank_account != "My business does not need a bank account") %>% # need to add this option
  mutate(not_answered = ifelse(reason_no_bank_account == "", 1, 0),
         documentation = ifelse(reason_no_bank_account == "Documentation (I do not have one or more of the required documents)", 1, 0),
         legal = ifelse(reason_no_bank_account == "My business is not legally registered.", 1, 0),
         finance = ifelse(reason_no_bank_account == "Affordability (The cost of using a bank account i.e., charges are too high for me)", 1, 0),
         trust = ifelse(reason_no_bank_account == "Insufficient security protocols (I do not feel my money is safe in the banking system)", 1, 0),
         bureaucracy = ifelse(reason_no_bank_account == "Bureaucracy (it takes too long to open an account and there are too many processes involved)", 1, 0),
         inappropriate = ifelse(reason_no_bank_account == "Distance (The bank is too far)", 1, 0),
         ) %>%
  group_by(across(all_of(level))) %>%
  summarise(# knowledge = sum(knowledge),
            documentation = sum(documentation),
            legal = sum(legal),
            finance = sum(finance),
            # law = sum(law),
            trust = sum(trust),
            bureaucracy = sum(bureaucracy),
            inappropriate = sum(inappropriate),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(# knowledge = knowledge / (responses - not_answered_reason),
         documentation_account = documentation / (responses - not_answered_reason),
         legal_account = legal / (responses - not_answered_reason),
         finance_account = finance / (responses - not_answered_reason),
         # law = law / (responses - not_answered_reason),
         trust_account = trust / (responses - not_answered_reason),
         bureaucracy_account = bureaucracy / (responses - not_answered_reason),
         inappropriate_account = inappropriate / (responses - not_answered_reason),
         
         documentation_account = ifelse(responses == not_answered_reason, 0 , documentation_account),
         legal_account = ifelse(responses == not_answered_reason, 0 , legal_account),
         finance_account = ifelse(responses == not_answered_reason, 0 , finance_account),
         trust_account = ifelse(responses == not_answered_reason, 0 , trust_account),
         bureaucracy_account = ifelse(responses == not_answered_reason, 0 , bureaucracy_account),
         inappropriate_account = ifelse(responses == not_answered_reason, o, inappropriate_account),
         )

bank_account %>%
  kable() %>%
  kable_styling()
```

```{r echo=FALSE}
sme_auction = data %>%
  select(all_of(level), 
         sme_foreign_exchange_auction, reason_not_sme_auction) %>%
  filter(sme_foreign_exchange_auction == "No") %>%
  # filter(reason_not_sme_auction != "I don’t need to register i.e. I don’t need FOREX" | reason_not_sme_auction != "I don’t see the need/ value") %>%
  mutate(not_answered = ifelse(reason_not_sme_auction == "", 1, 0),
         knowledge = ifelse(reason_not_sme_auction == "I am not aware of the auction system", 1, 0),
         legal = ifelse(reason_not_sme_auction == "My company does not qualify.", 1, 0),
         inappropriate = ifelse(reason_not_sme_auction == "The time frames do not meet my company’s needs.", 1, 0),
         law = ifelse(reason_not_sme_auction == "I don’t understand how it works – Language/Terminology used is difficult to understand.", 1, 0),
         trust = ifelse(reason_not_sme_auction == "I don’t trust the auction system", 1, 0)
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            # documentation = sum(documentation),
            legal = sum(legal),
            inappropriate = sum(inappropriate),
            law = sum(law),
            trust = sum(trust),
            # bureaucracy = sum(bureaucracy),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_sme = knowledge / (responses - not_answered_reason),
         # documentation_account = documentation / (responses - not_answered_reason),
         legal_sme = legal / (responses - not_answered_reason),
         inappropriate_sme = inappropriate / (responses - not_answered_reason),
         law_sme = law / (responses - not_answered_reason),
         trust_sme = trust / (responses - not_answered_reason),
         # bureaucracy_account = bureaucracy / (responses - not_answered_reason),
         
         knowledge_sme = ifelse(responses == not_answered_reason, 0 , knowledge_sme),
         legal_sme = ifelse(responses == not_answered_reason, 0 , legal_sme),
         inappropriate_sme = ifelse(responses == not_answered_reason, 0 , inappropriate_sme),
         law_sme = ifelse(responses == not_answered_reason, 0 , law_sme),
         trust_sme = ifelse(responses == not_answered_reason, 0 , trust_sme)
         )

sme_auction %>%
  kable() %>%
  kable_styling()
```

## Loans

```{r echo=FALSE}
commercial_loan = data %>%
  select(all_of(level), 
         commercial_loan_application, reason_not_apply_commercial_loan) %>%
  filter(commercial_loan_application == "No") %>%
  # filter() %>%
  mutate(not_answered = ifelse(reason_not_apply_commercial_loan == "", 1, 0),
         knowledge = ifelse(reason_not_apply_commercial_loan == "I don’t have information on how I can apply for a loan.", 1, 0),
         documentation = ifelse(reason_not_apply_commercial_loan == "I don’t meet the documentation requirements.", 1, 0),
         legal = ifelse(reason_not_apply_commercial_loan == "I don’t have sufficient collateral.", 1, 0),
         finance = ifelse(reason_not_apply_commercial_loan == "Cost (interest rates are too high)", 1, 0),
         inappropriate = ifelse(reason_not_apply_commercial_loan == "It is not a product being offered by my bank.", 1, 0)
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            documentation = sum(documentation),
            legal = sum(legal),
            finance = sum(finance),
            # law = sum(law),
            # trust = sum(trust),
            # bureaucracy = sum(bureaucracy),
            inappropriate = sum(inappropriate),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_commercial_loan = knowledge / (responses - not_answered_reason),
         documentation_commercial_loan = documentation / (responses - not_answered_reason),
         legal_commercial_loan = legal / (responses - not_answered_reason),
         finance_commercial_loan = finance / (responses - not_answered_reason),
         # law_sme = law / (responses - not_answered_reason),
         # trust_sme = trust / (responses - not_answered_reason),
         # bureaucracy_account = bureaucracy / (responses - not_answered_reason),
         inappropriate_commercial_loan = inappropriate / (responses - not_answered_reason),
         
         knowledge_commercial_loan = ifelse(responses == not_answered_reason, 0 , knowledge_commercial_loan),
         documentation_commercial_loan = ifelse(responses == not_answered_reason, 0 , documentation_commercial_loan),
         legal_commercial_loan = ifelse(responses == not_answered_reason, 0 , legal_commercial_loan),
         finance_commercial_loan = ifelse(responses == not_answered_reason, 0 , finance_commercial_loan),
         inappropriate_commercial_loan = ifelse(responses == not_answered_reason, 0 , inappropriate_commercial_loan),
         )

commercial_loan %>%
  kable() %>%
  kable_styling()
```

## Insurance

```{r echo=FALSE}
business_insurance = data %>%
  select(all_of(level), 
         insurance_business_products, reason_no_insurance_products_services) %>%
  filter(insurance_business_products == "No") %>%
  # filter(I don’t see the need/ value.) %>%
  mutate(not_answered = ifelse(reason_no_insurance_products_services == "", 1, 0),
         knowledge = ifelse(reason_no_insurance_products_services == "I am not aware of the insurance products.", 1, 0),
         legal = ifelse(reason_no_insurance_products_services == "My company does not qualify.", 1, 0),
         finance = ifelse(reason_no_insurance_products_services == "The products are unaffordable", 1, 0),
         inflation = ifelse(reason_no_insurance_products_services == "Inflation(The sum assured loses value)", 1, 0),
         law = ifelse(reason_no_insurance_products_services == "I don’t understand how it works – Language/Terminology used is difficult to understand.", 1, 0),
         trust = ifelse(reason_no_insurance_products_services == "I don’t trust insurance companies.", 1, 0),
         inappropriate = ifelse(reason_no_insurance_products_services == "The insurance products do not meet my company’s needs.", 1, 0)
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            # documentation = sum(documentation),
            legal = sum(legal),
            finance = sum(finance),
            inflation = sum(inflation),
            law = sum(law),
            trust = sum(trust),
            # bureaucracy = sum(bureaucracy),
            inappropriate = sum(inappropriate),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_insurance = knowledge / (responses - not_answered_reason),
         # documentation_insurance = documentation / (responses - not_answered_reason),
         legal_insurance = legal / (responses - not_answered_reason),
         finance_insurance = finance / (responses - not_answered_reason),
         inflation_insurance = inflation / (responses - not_answered_reason),
         law_insurance = law / (responses - not_answered_reason),
         trust_insurance = trust / (responses - not_answered_reason),
         # bureaucracy_insurance = bureaucracy / (responses - not_answered_reason),
         inappropriate_insurance = inappropriate / (responses - not_answered_reason),
         
         knowledge_insurance = ifelse(responses == not_answered_reason, 0 , knowledge_insurance),
         legal_insurance = ifelse(responses == not_answered_reason, 0 , legal_insurance),
         finance_insurance = ifelse(responses == not_answered_reason, 0 , finance_insurance),
         inflation_insurance = ifelse(responses == not_answered_reason, 0 , inflation_insurance),
         law_insurance = ifelse(responses == not_answered_reason, 0 , law_insurance),
         trust_insurance = ifelse(responses == not_answered_reason, 0 , trust_insurance),
         inappropriate_insurance = ifelse(responses == not_answered_reason, 0 , inappropriate_insurance),
         )

business_insurance %>%
  kable() %>%
  kable_styling()
```

## Pensions

```{r echo=FALSE}
pension = data %>%
  select(all_of(level), 
         pension_policy, reason_no_pension_policy) %>%
  filter(pension_policy == "No") %>%
  # filter(I don’t see the need/ value.) %>%
  mutate(not_answered = ifelse(reason_no_pension_policy == "", 1, 0),
         knowledge = ifelse(reason_no_pension_policy == "I am not aware of the pensions products.", 1, 0),
         finance = ifelse(reason_no_pension_policy == "The products are too expensive.", 1, 0),
         inflation = ifelse(reason_no_pension_policy == "Inflation", 1, 0),
         law = ifelse(reason_no_pension_policy == "I don’t understand how it works – Language/Terminology used is difficult to understand.", 1, 0),
         trust = ifelse(reason_no_pension_policy == "I don’t trust service providers companies.", 1, 0),
         inappropriate = ifelse(reason_no_pension_policy == "The products do not meet my company’s needs.", 1, 0)
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            # documentation = sum(documentation),
            # legal = sum(legal),
            finance = sum(finance),
            inflation = sum(inflation),
            law = sum(law),
            trust = sum(trust),
            # bureaucracy = sum(bureaucracy),
            inappropriate = sum(inappropriate),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_pensions = knowledge / (responses - not_answered_reason),
         # documentation_pensions = documentation / (responses - not_answered_reason),
         # legal_pensions = legal / (responses - not_answered_reason),
         finance_pensions = finance / (responses - not_answered_reason),
         inflation_pensions = inflation / (responses - not_answered_reason),
         law_pensions = law / (responses - not_answered_reason),
         trust_insurance = trust / (responses - not_answered_reason),
         # bureaucracy_pensions = bureaucracy / (responses - not_answered_reason),
         inappropriate_pensions = inappropriate / (responses - not_answered_reason),
         
         knowledge_pensions = ifelse(responses == not_answered_reason, 0 , knowledge_pensions),
         finance_pensions = ifelse(responses == not_answered_reason, 0 , finance_pensions),
         inflation_pensions = ifelse(responses == not_answered_reason, 0 , inflation_pensions),
         law_pensions = ifelse(responses == not_answered_reason, 0 , law_pensions),
         trust_pensions = ifelse(responses == not_answered_reason, 0 , trust_insurance),
         inappropriate_pensions = ifelse(responses == not_answered_reason, 0 , inappropriate_pensions),
         )

pension %>%
  kable() %>%
  kable_styling()
```

## Mobile Money

```{r echo=FALSE}
mobile_money = data %>%
  select(all_of(level), 
         mobile_money_account, reason_no_mobile_money_account) %>%
  filter(mobile_money_account == "No") %>%
  # filter(My business does not need a mobile money account (because we only/mainly handle cash transactions)) %>%
  mutate(not_answered = ifelse(reason_no_mobile_money_account == "", 1, 0),
         documentation = ifelse(reason_no_mobile_money_account == "Documentation (I do not have one or more of the required documents)", 1, 0),
         finance = ifelse(reason_no_mobile_money_account == "Affordability (The charges are too high)", 1, 0),
         trust = ifelse(reason_no_mobile_money_account == "Insufficient security protocols (I do not feel my money is safe in the mobile money system)", 1, 0),
         bureaucracy = ifelse(reason_no_mobile_money_account == "Bureaucracy (it takes too long to open an account and there are too many processes involved)", 1, 0)
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise(# knowledge = sum(knowledge),
            documentation = sum(documentation),
            # legal = sum(legal),
            finance = sum(finance),
            # law = sum(law),
            trust = sum(trust),
            bureaucracy = sum(bureaucracy),
            # inappropriate = sum(inappropriate),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(# knowledge_mobile = knowledge / (responses - not_answered_reason),
         documentation_mobile = documentation / (responses - not_answered_reason),
         # legal_mobile = legal / (responses - not_answered_reason),
         finance_mobile = finance / (responses - not_answered_reason),
         # law_mobile = law / (responses - not_answered_reason),
         trust_mobile = trust / (responses - not_answered_reason),
         bureaucracy_mobile = bureaucracy / (responses - not_answered_reason),
         # inappropriate_mobile = inappropriate / (responses - not_answered_reason),
         
         documentation_mobile = ifelse(responses == not_answered_reason, 0 , documentation_mobile),
         finance_mobile = ifelse(responses == not_answered_reason, 0 , finance_mobile),
         trust_mobile = ifelse(responses == not_answered_reason, 0 , trust_mobile),
         bureaucracy_mobile = ifelse(responses == not_answered_reason, 0 , bureaucracy_mobile)
         )

mobile_money %>%
  kable() %>%
  kable_styling()
```

## Savings facility

```{r echo=FALSE}
investments = data %>%
  select(all_of(level), 
         investments, reason_no_investments) %>%
  filter(investments == "No") %>%
  # filter(My business does not need a mobile money account (because we only/mainly handle cash transactions)) %>%
  mutate(not_answered = ifelse(reason_no_investments == "", 1, 0),
         knowledge = ifelse(reason_no_investments == "I am not aware of any investment products.", 1, 0),
         finance = ifelse(reason_no_investments == "Inadequate cash flows for investment", 1, 0),
         inflation = ifelse(reason_no_investments == "Inflation", 1, 0),
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            # documentation = sum(documentation),
            # legal = sum(legal),
            finance = sum(finance),
            inflation = sum(inflation),
            # law = sum(law),
            # trust = sum(trust),
            # bureaucracy = sum(bureaucracy),
            # inappropriate = sum(inappropriate),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_investments = knowledge / (responses - not_answered_reason),
         # documentation_investments = documentation / (responses - not_answered_reason),
         # legal_investments = legal / (responses - not_answered_reason),
         finance_investments = finance / (responses - not_answered_reason),
         inflation_investments = inflation / (responses - not_answered_reason),
         # law_investments = law / (responses - not_answered_reason),
         # trust_investments = trust / (responses - not_answered_reason),
         # bureaucracy_investments = bureaucracy / (responses - not_answered_reason),
         # inappropriate_investments = inappropriate / (responses - not_answered_reason),
         
         knowledge_investments = ifelse(responses == not_answered_reason, 0 , knowledge_investments),
         finance_investments = ifelse(responses == not_answered_reason, 0 , finance_investments),
         inflation_investments = ifelse(responses == not_answered_reason, 0 , inflation_investments),
         )

investments %>%
  kable() %>%
  kable_styling()
```

## Access to information


## Combine into 8 measures

```{r echo=FALSE}
reasons = 
  register %>% select(all_of(level), knowledge_register, finance_register, law_register, bureaucracy_register) %>%
  full_join((zimra %>% select(all_of(level), knowledge_zimra, finance_zimra, inflation_zimra, law_zimra, bureaucracy_zimra)), 
            by = all_of(level)) %>%
  full_join((bank_account %>% select(all_of(level), documentation_account, legal_account, finance_account, trust_account, bureaucracy_account, inappropriate_account)),
            by = all_of(level)) %>%
  full_join((sme_auction %>% select(all_of(level), knowledge_sme, legal_sme, law_sme, trust_sme, inappropriate_sme)),
            by = all_of(level)) %>%
  full_join((commercial_loan %>% select(all_of(level), knowledge_commercial_loan, documentation_commercial_loan,legal_commercial_loan,finance_commercial_loan,inappropriate_commercial_loan)),
            by = all_of(level)) %>%
  full_join((business_insurance %>% select(all_of(level), knowledge_insurance,legal_insurance,finance_insurance,inflation_insurance, law_insurance,trust_insurance,inappropriate_insurance)),
            by = all_of(level)) %>%
  full_join((pension %>% select(all_of(level), knowledge_pensions,finance_pensions, inflation_pensions, law_pensions,trust_pensions,inappropriate_pensions)),
            by = all_of(level)) %>%
  full_join((mobile_money %>% select(all_of(level), documentation_mobile,finance_mobile,trust_mobile,bureaucracy_mobile)),
            by = all_of(level)) %>%
  full_join((investments %>% select(all_of(level),knowledge_investments, finance_investments, inflation_investments)),
            by = all_of(level))


barrier_reasons = reasons %>%
  mutate(knowledge = rowMeans(reasons[, 
                                      c("knowledge_register", "knowledge_zimra", "knowledge_sme", "knowledge_commercial_loan", "knowledge_insurance", "knowledge_pensions", "knowledge_investments")]),
         documentation = rowMeans(reasons[, 
                                          c("documentation_account", "documentation_commercial_loan", "documentation_mobile")]),
         legal = rowMeans(reasons[, 
                                  c("legal_account", "legal_sme", "legal_commercial_loan", "legal_insurance")]),
         finance = rowMeans(reasons[, 
                                    c("finance_register", "finance_zimra", "finance_account", "finance_commercial_loan", "finance_insurance", "finance_pensions", "finance_mobile", "finance_investments")]),
         inflation = rowMeans(reasons[,
                                      c("inflation_zimra", "inflation_insurance", "inflation_pensions", "inflation_investments")]),
         law = rowMeans(reasons[, 
                                c("law_register", "law_zimra", "law_sme", "law_insurance", "law_pensions")]),
         trust = rowMeans(reasons[, 
                                  c("trust_account", "trust_sme", "trust_insurance", "trust_pensions", "trust_mobile")]),
         bureaucracy = rowMeans(reasons[, 
                                        c("bureaucracy_register", "bureaucracy_zimra", "bureaucracy_account", "bureaucracy_mobile")]),
         inappropraite = rowMeans(reasons[, 
                                          c("inappropriate_account", "inappropriate_sme", "inappropriate_commercial_loan", "inappropriate_insurance", "inappropriate_pensions")]),
         )

```

## Knowledge score

- Very good: 5

- Good: 4

- Average: 3

- Poor: 2

- Very poor: 1

- I don't know anything: 0

```{r echo=FALSE}
# Knowledge score... each out of 5
knowledge_score = data %>%
  select(all_of(level),
         knowledge_banking_services, knowledge_mobile_money_services, knowledge_investements_capital_markets,
         knowledge_business_insurance_products, knowledge_pension_products, knowledge_loans_credit_commercial_banks,
         knowledge_loans_credit_microfinance, knowledge_loans_credit_roscas_isals, knowledge_taxation_regulations) %>%
  mutate(not_answered_banking = ifelse(knowledge_banking_services == "", 1, 0),
         not_answered_mobile = ifelse(knowledge_mobile_money_services == "", 1, 0),
         not_answered_investments = ifelse(knowledge_investements_capital_markets == "", 1, 0),
         not_answered_insurance = ifelse(knowledge_business_insurance_products == "", 1, 0),
         not_answered_pensions = ifelse(knowledge_pension_products == "", 1, 0),
         not_answered_commercial_loan = ifelse(knowledge_loans_credit_commercial_banks == "", 1, 0),
         not_answered_mfi_loan = ifelse(knowledge_loans_credit_microfinance == "", 1, 0),
         not_answered_rosal_loan = ifelse(knowledge_loans_credit_roscas_isals == "", 1, 0),
         not_answered_tax = ifelse(knowledge_taxation_regulations == "", 1, 0),
         
         
         knowledge_banking_services = case_when(
    knowledge_banking_services == "Very good" ~ 5,
    knowledge_banking_services == "Good" ~ 4,
    knowledge_banking_services == "Average" ~ 3,
    knowledge_banking_services == "Poor" ~ 2,
    knowledge_banking_services == "Very poor" ~ 1,
    knowledge_banking_services == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_mobile_money_services = case_when(
    knowledge_mobile_money_services == "Very good" ~ 5,
    knowledge_mobile_money_services == "Good" ~ 4,
    knowledge_mobile_money_services == "Average" ~ 3,
    knowledge_mobile_money_services == "Poor" ~ 2,
    knowledge_mobile_money_services == "Very poor" ~ 1,
    knowledge_mobile_money_services == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_investements_capital_markets = case_when(
    knowledge_investements_capital_markets == "Very good" ~ 5,
    knowledge_investements_capital_markets == "Good" ~ 4,
    knowledge_investements_capital_markets == "Average" ~ 3,
    knowledge_investements_capital_markets == "Poor" ~ 2,
    knowledge_investements_capital_markets == "Very poor" ~ 1,
    knowledge_investements_capital_markets == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_business_insurance_products = case_when(
    knowledge_business_insurance_products == "Very good" ~ 5,
    knowledge_business_insurance_products == "Good" ~ 4,
    knowledge_business_insurance_products == "Average" ~ 3,
    knowledge_business_insurance_products == "Poor" ~ 2,
    knowledge_business_insurance_products == "Very poor" ~ 1,
    knowledge_business_insurance_products == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_pension_products = case_when(
    knowledge_pension_products == "Very good" ~ 5,
    knowledge_pension_products == "Good" ~ 4,
    knowledge_pension_products == "Average" ~ 3,
    knowledge_pension_products == "Poor" ~ 2,
    knowledge_pension_products == "Very poor" ~ 1,
    knowledge_pension_products == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_loans_credit_commercial_banks = case_when(
    knowledge_loans_credit_commercial_banks == "Very good" ~ 5,
    knowledge_loans_credit_commercial_banks == "Good" ~ 4,
    knowledge_loans_credit_commercial_banks == "Average" ~ 3,
    knowledge_loans_credit_commercial_banks == "Poor" ~ 2,
    knowledge_loans_credit_commercial_banks == "Very poor" ~ 1,
    knowledge_loans_credit_commercial_banks == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_loans_credit_microfinance = case_when(
    knowledge_loans_credit_microfinance == "Very good" ~ 5,
    knowledge_loans_credit_microfinance == "Good" ~ 4,
    knowledge_loans_credit_microfinance == "Average" ~ 3,
    knowledge_loans_credit_microfinance == "Poor" ~ 2,
    knowledge_loans_credit_microfinance == "Very poor" ~ 1,
    knowledge_loans_credit_microfinance == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_loans_credit_roscas_isals = case_when(
    knowledge_loans_credit_roscas_isals == "Very good" ~ 5,
    knowledge_loans_credit_roscas_isals == "Good" ~ 4,
    knowledge_loans_credit_roscas_isals == "Average" ~ 3,
    knowledge_loans_credit_roscas_isals == "Poor" ~ 2,
    knowledge_loans_credit_roscas_isals == "Very poor" ~ 1,
    knowledge_loans_credit_roscas_isals == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_taxation_regulations = case_when(
    knowledge_taxation_regulations == "Very good" ~ 5,
    knowledge_taxation_regulations == "Good" ~ 4,
    knowledge_taxation_regulations == "Average" ~ 3,
    knowledge_taxation_regulations == "Poor" ~ 2,
    knowledge_taxation_regulations == "Very poor" ~ 1,
    knowledge_taxation_regulations == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  )
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise_if(is.numeric, sum) %>%
  mutate(responses = provincial_totals)

knowledge_score$not_answered = rowSums(knowledge_score[, c("not_answered_banking", "not_answered_mobile", "not_answered_investments",
                                                           "not_answered_insurance", "not_answered_pensions", "not_answered_commercial_loan",
                                                           "not_answered_mfi_loan", "not_answered_rosal_loan", "not_answered_tax")])

knowledge_score$score = rowSums(knowledge_score[, c("knowledge_banking_services", "knowledge_mobile_money_services", "knowledge_investements_capital_markets",
         "knowledge_business_insurance_products", "knowledge_pension_products", "knowledge_loans_credit_commercial_banks",
         "knowledge_loans_credit_microfinance", "knowledge_loans_credit_roscas_isals", "knowledge_taxation_regulations")])

knowledge_score_final = knowledge_score %>%
  mutate(max_score = (5* (responses - not_answered)) * 9,
         score_value = score / max_score
         )

knowledge_score_final %>%
  kable() %>%
  kable_styling()
```

```{r}
barriers_critera = data %>%
  group_by(across(all_of(level))) %>%
  summarise(n=n()) %>%
  full_join(y = (barrier_reasons %>% select(all_of(level), knowledge, documentation, legal, finance, inflation, law, trust, bureaucracy, inappropraite)), by = all_of(level)) %>%
  full_join(y = (knowledge_score_final %>% select(all_of(level), score_value)))

barriers_critera %>%
  kable() %>%
  kable_styling()
```


```{r}
write.csv(barriers_critera, file = "~/SIVIOgit/barriers_criteria.csv")
```

```{r}
# data %>%
#   select(
#     # characteristics
#     
#     # registration
#     
#     # banking
#     barriers_use_bank_account,
#     restrictions_bank_account,
#     
#     # loans
#     reason_rejected_commercial_loan_12months,
#     
#     # other financial institutions
#     
#     # insurance
#     
#     # pensions
#     
#     # mobile money
#     barriers_use_mobile_money,
#     restrictions_use_mobile_money,
#     
#     # investments
#     
#     # access to information
#     
#   )
```