---
title: "barriers"
author: "Beks"
date: "10/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(kableExtra)
```

```{r}
data = read.csv(file = "~/SIVIOgit/clean_FI_2021.csv")
# data = read.csv(file = "~/SIVIOgit/data_equal_comparisons.csv")
```

# levels of inclusion.

This can be used to compare across the different measures.

```{r}
level = c("province"
          # ,"gender_inclusion"
          # ,"location_inclusion"
          # ,"size_inclusion"
          # ,"age_inclusion"
          # ,"formality_inclusion"
          # ,"sector_inclusion"
          )
```

```{r include=FALSE}
# Reasons
reason = c("knowledge",
             "documentation",
             "legal",
             "finance",
             "trust",
             "inflation",
             "bureaucracy",
             "law",
             "inappropriate")

# Criteria
criteria = c("reason", 
             # "score_value",
             "restrictions_bank_account_value",
             "restrictions_mobile_money_value")

nreason = length(reasons)
ncriteria = length(criteria)
```

There are `r nreason` reasons for not having or using financial products/services

These reasons are: `r reason`

There are `r ncriteria` criteria which are `r criteria`

```{r include=FALSE}
provincial_totals = data %>% group_by(across(all_of(level))) %>% summarise(provincial_totals = n())
```


# Penetration Barriers

## Registration 

- not registered

- not registered with ZIMRA

**Knowledge, Finance/Affordability, Complicated law, Bureaucracy**

```{r echo=FALSE}
register = data %>%
  select(all_of(level), 
         registered, reason_not_registered) %>%
  filter(registered == "No") %>%
  # filter(reason_not_registered != "I simply do not want to register.") %>%
  mutate(not_answered = ifelse(reason_not_registered == "", 1, 0),
         knowledge = ifelse(reason_not_registered == "I do not know how to register.", 1, 0),
         finance = ifelse(reason_not_registered == "It costs too much", 1, 0),
         law = ifelse(reason_not_registered == "Lack of simplicity and accuracy of the company registration law", 1, 0),
         bureaucracy = ifelse(reason_not_registered == "The process is bureaucratic.", 1, 0)
         ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            finance = sum(finance),
            law = sum(law),
            bureaucracy = sum(bureaucracy),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_register = knowledge / (responses - not_answered_reason),
         finance_register = finance / (responses - not_answered_reason),
         law_register = law / (responses - not_answered_reason),
         bureaucracy_register = bureaucracy / (responses - not_answered_reason)) %>%
  full_join(y = provincial_totals, by = all_of(level))

register$reasons = rowSums(register[, c("knowledge", "finance", "law", "bureaucracy")])

register$reasons_register = register$reasons / (register$provincial_totals - register$not_answered_reason)

register %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

```{r echo=FALSE}
zimra = data %>%
  select(all_of(level), 
         zimra_registration, reason_not_zimra) %>%
  filter(zimra_registration == "None of the above")%>%
  # filter(reason_not_zimra != "I don’t need any of the above to operate") %>%
  mutate(not_answered = ifelse(reason_not_zimra == "", 1, 0),
         knowledge = ifelse(reason_not_zimra == "I do not know how to register.", 1, 0),
         finance = ifelse(reason_not_zimra == "Taxes are too high.", 1, 0),
         inflation = ifelse(reason_not_zimra == "Inflation", 1, 0),
         law = ifelse(reason_not_zimra == "Lack of simplicity and accuracy of the tax legislation", 1, 0),
         bureaucracy = ifelse(reason_not_zimra == "The process is bureaucratic.", 1, 0)
         ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            finance = sum(finance),
            inflation = sum(inflation),
            law = sum(law),
            bureaucracy = sum(bureaucracy),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_zimra = knowledge / (responses - not_answered_reason),
         finance_zimra = finance / (responses - not_answered_reason),
         inflation_zimra = inflation / (responses - not_answered_reason),
         law_zimra = law / (responses - not_answered_reason),
         bureaucracy_zimra = bureaucracy / (responses - not_answered_reason),
         
         knowledge_zimra = ifelse(responses == not_answered_reason, 0 , knowledge_zimra),
         finance_zimra = ifelse(responses == not_answered_reason, 0 , finance_zimra),
         inflation_zimra = ifelse(responses == not_answered_reason, 0 , inflation_zimra),
         law_zimra = ifelse(responses == not_answered_reason, 0 , law_zimra),
         bureaucracy_zimra = ifelse(responses == not_answered_reason, 0 , bureaucracy_zimra),
         )%>%
  full_join(y = provincial_totals, by = all_of(level))

zimra$reasons = rowSums(zimra[, c("knowledge", "finance","inflation", "law", "bureaucracy")])

zimra$reasons_zimra = zimra$reasons / (zimra$provincial_totals - zimra$not_answered_reason)

zimra %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```


## Banking

- reason no bank account

**Documentation, legal standing, finance, trust, bureaucracy**

- reason not registered on SME auction

**Knowledge, legal standing, finance, Complicated law, trust**

- faced restrictions in use of bank account

```{r echo=FALSE}
bank_account = data %>%
  select(all_of(level), 
         bank_account, reason_no_bank_account) %>%
  filter(bank_account == "No") %>%
  # filter(reason_no_bank_account != "My business does not need a bank account") %>% # need to add this option
  mutate(not_answered = ifelse(reason_no_bank_account == "", 1, 0),
         documentation = ifelse(reason_no_bank_account == "Documentation (I do not have one or more of the required documents)", 1, 0),
         legal = ifelse(reason_no_bank_account == "My business is not legally registered.", 1, 0),
         finance = ifelse(reason_no_bank_account == "Affordability (The cost of using a bank account i.e., charges are too high for me)", 1, 0),
         trust = ifelse(reason_no_bank_account == "Insufficient security protocols (I do not feel my money is safe in the banking system)", 1, 0),
         bureaucracy = ifelse(reason_no_bank_account == "Bureaucracy (it takes too long to open an account and there are too many processes involved)", 1, 0),
         inappropriate = ifelse(reason_no_bank_account == "Distance (The bank is too far)", 1, 0),
         ) %>%
  group_by(across(all_of(level))) %>%
  summarise(documentation = sum(documentation),
            legal = sum(legal),
            finance = sum(finance),
            trust = sum(trust),
            bureaucracy = sum(bureaucracy),
            inappropriate = sum(inappropriate),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(documentation_account = documentation / (responses - not_answered_reason),
         legal_account = legal / (responses - not_answered_reason),
         finance_account = finance / (responses - not_answered_reason),
         trust_account = trust / (responses - not_answered_reason),
         bureaucracy_account = bureaucracy / (responses - not_answered_reason),
         inappropriate_account = inappropriate / (responses - not_answered_reason),
         
         documentation_account = ifelse(responses == not_answered_reason, 0 , documentation_account),
         legal_account = ifelse(responses == not_answered_reason, 0 , legal_account),
         finance_account = ifelse(responses == not_answered_reason, 0 , finance_account),
         trust_account = ifelse(responses == not_answered_reason, 0 , trust_account),
         bureaucracy_account = ifelse(responses == not_answered_reason, 0 , bureaucracy_account),
         inappropriate_account = ifelse(responses == not_answered_reason, o, inappropriate_account),
         )%>%
  full_join(y = provincial_totals, by = all_of(level))

bank_account$reasons = rowSums(bank_account[, c("documentation", "legal", "finance", "trust", "bureaucracy", "inappropriate")])

bank_account$reasons_account = bank_account$reasons / (bank_account$provincial_totals - bank_account$not_answered_reason)

bank_account %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

```{r echo=FALSE}
sme_auction = data %>%
  select(all_of(level), 
         sme_foreign_exchange_auction, reason_not_sme_auction) %>%
  filter(sme_foreign_exchange_auction == "No") %>%
  # filter(reason_not_sme_auction != "I don’t need to register i.e. I don’t need FOREX" | reason_not_sme_auction != "I don’t see the need/ value") %>%
  mutate(not_answered = ifelse(reason_not_sme_auction == "", 1, 0),
         knowledge = ifelse(reason_not_sme_auction == "I am not aware of the auction system", 1, 0),
         legal = ifelse(reason_not_sme_auction == "My company does not qualify.", 1, 0),
         inappropriate = ifelse(reason_not_sme_auction == "The time frames do not meet my company’s needs.", 1, 0),
         law = ifelse(reason_not_sme_auction == "I don’t understand how it works – Language/Terminology used is difficult to understand.", 1, 0),
         trust = ifelse(reason_not_sme_auction == "I don’t trust the auction system", 1, 0)
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            legal = sum(legal),
            inappropriate = sum(inappropriate),
            law = sum(law),
            trust = sum(trust),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_sme = knowledge / (responses - not_answered_reason),
         legal_sme = legal / (responses - not_answered_reason),
         inappropriate_sme = inappropriate / (responses - not_answered_reason),
         law_sme = law / (responses - not_answered_reason),
         trust_sme = trust / (responses - not_answered_reason),
         
         knowledge_sme = ifelse(responses == not_answered_reason, 0 , knowledge_sme),
         legal_sme = ifelse(responses == not_answered_reason, 0 , legal_sme),
         inappropriate_sme = ifelse(responses == not_answered_reason, 0 , inappropriate_sme),
         law_sme = ifelse(responses == not_answered_reason, 0 , law_sme),
         trust_sme = ifelse(responses == not_answered_reason, 0 , trust_sme)
         )%>%
  full_join(y = provincial_totals, by = all_of(level))

sme_auction$reasons = rowSums(sme_auction[, c("knowledge", "legal", "inappropriate", "law", "trust")])

sme_auction$reasons_sme = sme_auction$reasons / (sme_auction$provincial_totals - sme_auction$not_answered_reason)

sme_auction %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

```{r echo=FALSE}
# restrictions in use of bank account
restrictions_bank_account = data %>%
  select(all_of(level),
         bank_account, restrictions_bank_account) %>%
  filter(bank_account == "Yes") %>%
  mutate(not_answered = ifelse(restrictions_bank_account == "", 1, 0),
         restrictions_bank_use_logic = ifelse(restrictions_bank_account == "Yes", 1, 0)) %>%
  group_by(across(all_of(level))) %>%
  summarise(restrictions_bank_account = sum(restrictions_bank_use_logic),
            responses = n(),
            not_answered_restrictions_bank = sum(not_answered)) %>%
  mutate(restrictions_bank_account_value = restrictions_bank_account / (responses - not_answered_restrictions_bank))

restrictions_bank_account %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

## Loans

- reasons not applied for a loan in the past

**knowledge, documentation, legal, finance, appropriateness**

```{r echo=FALSE}
commercial_loan = data %>%
  select(all_of(level), 
         commercial_loan_application, reason_not_apply_commercial_loan) %>%
  filter(commercial_loan_application == "No") %>%
  # filter() %>%
  mutate(not_answered = ifelse(reason_not_apply_commercial_loan == "", 1, 0),
         knowledge = ifelse(reason_not_apply_commercial_loan == "I don’t have information on how I can apply for a loan.", 1, 0),
         documentation = ifelse(reason_not_apply_commercial_loan == "I don’t meet the documentation requirements.", 1, 0),
         legal = ifelse(reason_not_apply_commercial_loan == "I don’t have sufficient collateral.", 1, 0),
         finance = ifelse(reason_not_apply_commercial_loan == "Cost (interest rates are too high)", 1, 0),
         inappropriate = ifelse(reason_not_apply_commercial_loan == "It is not a product being offered by my bank.", 1, 0)
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            documentation = sum(documentation),
            legal = sum(legal),
            finance = sum(finance),
            inappropriate = sum(inappropriate),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_commercial_loan = knowledge / (responses - not_answered_reason),
         documentation_commercial_loan = documentation / (responses - not_answered_reason),
         legal_commercial_loan = legal / (responses - not_answered_reason),
         finance_commercial_loan = finance / (responses - not_answered_reason),
         inappropriate_commercial_loan = inappropriate / (responses - not_answered_reason),
         
         knowledge_commercial_loan = ifelse(responses == not_answered_reason, 0 , knowledge_commercial_loan),
         documentation_commercial_loan = ifelse(responses == not_answered_reason, 0 , documentation_commercial_loan),
         legal_commercial_loan = ifelse(responses == not_answered_reason, 0 , legal_commercial_loan),
         finance_commercial_loan = ifelse(responses == not_answered_reason, 0 , finance_commercial_loan),
         inappropriate_commercial_loan = ifelse(responses == not_answered_reason, 0 , inappropriate_commercial_loan),
         )%>%
  full_join(y = provincial_totals, by = all_of(level))

commercial_loan$reasons = rowSums(commercial_loan[, c("knowledge","documentation", "legal", "finance", "inappropriate")])

commercial_loan$reasons_loan = commercial_loan$reasons / (commercial_loan$provincial_totals - commercial_loan$not_answered_reason)

commercial_loan %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

## Insurance

- reasons not having business insurance products

**knowledge, legal standing, finance, inflation, law, trust, appropriateness**

```{r echo=FALSE}
business_insurance = data %>%
  select(all_of(level), 
         insurance_business_products, reason_no_insurance_products_services) %>%
  filter(insurance_business_products == "No") %>%
  # filter(I don’t see the need/ value.) %>%
  mutate(not_answered = ifelse(reason_no_insurance_products_services == "", 1, 0),
         knowledge = ifelse(reason_no_insurance_products_services == "I am not aware of the insurance products.", 1, 0),
         legal = ifelse(reason_no_insurance_products_services == "My company does not qualify.", 1, 0),
         finance = ifelse(reason_no_insurance_products_services == "The products are unaffordable", 1, 0),
         inflation = ifelse(reason_no_insurance_products_services == "Inflation(The sum assured loses value)", 1, 0),
         law = ifelse(reason_no_insurance_products_services == "I don’t understand how it works – Language/Terminology used is difficult to understand.", 1, 0),
         trust = ifelse(reason_no_insurance_products_services == "I don’t trust insurance companies.", 1, 0),
         inappropriate = ifelse(reason_no_insurance_products_services == "The insurance products do not meet my company’s needs.", 1, 0)
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            legal = sum(legal),
            finance = sum(finance),
            inflation = sum(inflation),
            law = sum(law),
            trust = sum(trust),
            inappropriate = sum(inappropriate),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_insurance = knowledge / (responses - not_answered_reason),
         legal_insurance = legal / (responses - not_answered_reason),
         finance_insurance = finance / (responses - not_answered_reason),
         inflation_insurance = inflation / (responses - not_answered_reason),
         law_insurance = law / (responses - not_answered_reason),
         trust_insurance = trust / (responses - not_answered_reason),
         inappropriate_insurance = inappropriate / (responses - not_answered_reason),
         
         knowledge_insurance = ifelse(responses == not_answered_reason, 0 , knowledge_insurance),
         legal_insurance = ifelse(responses == not_answered_reason, 0 , legal_insurance),
         finance_insurance = ifelse(responses == not_answered_reason, 0 , finance_insurance),
         inflation_insurance = ifelse(responses == not_answered_reason, 0 , inflation_insurance),
         law_insurance = ifelse(responses == not_answered_reason, 0 , law_insurance),
         trust_insurance = ifelse(responses == not_answered_reason, 0 , trust_insurance),
         inappropriate_insurance = ifelse(responses == not_answered_reason, 0 , inappropriate_insurance),
         )%>%
  full_join(y = provincial_totals, by = all_of(level))

business_insurance$reasons = rowSums(business_insurance[, c("knowledge", "legal", "finance", "inflation", "law", "trust", "inappropriate")])

business_insurance$reasons_insurance = business_insurance$reasons / (business_insurance$provincial_totals - business_insurance$not_answered_reason)

business_insurance %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

## Pensions

- reasons not having a pension policy

**knowledge, finance, inflation, law, trust, appropriateness**

```{r echo=FALSE}
pension = data %>%
  select(all_of(level), 
         pension_policy, reason_no_pension_policy) %>%
  filter(pension_policy == "No") %>%
  # filter(I don’t see the need/ value.) %>%
  mutate(not_answered = ifelse(reason_no_pension_policy == "", 1, 0),
         knowledge = ifelse(reason_no_pension_policy == "I am not aware of the pensions products.", 1, 0),
         finance = ifelse(reason_no_pension_policy == "The products are too expensive.", 1, 0),
         inflation = ifelse(reason_no_pension_policy == "Inflation", 1, 0),
         law = ifelse(reason_no_pension_policy == "I don’t understand how it works – Language/Terminology used is difficult to understand.", 1, 0),
         trust = ifelse(reason_no_pension_policy == "I don’t trust service providers companies.", 1, 0),
         inappropriate = ifelse(reason_no_pension_policy == "The products do not meet my company’s needs.", 1, 0)
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            finance = sum(finance),
            inflation = sum(inflation),
            law = sum(law),
            trust = sum(trust),
            inappropriate = sum(inappropriate),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_pensions = knowledge / (responses - not_answered_reason),
         finance_pensions = finance / (responses - not_answered_reason),
         inflation_pensions = inflation / (responses - not_answered_reason),
         law_pensions = law / (responses - not_answered_reason),
         trust_insurance = trust / (responses - not_answered_reason),
         inappropriate_pensions = inappropriate / (responses - not_answered_reason),
         
         knowledge_pensions = ifelse(responses == not_answered_reason, 0 , knowledge_pensions),
         finance_pensions = ifelse(responses == not_answered_reason, 0 , finance_pensions),
         inflation_pensions = ifelse(responses == not_answered_reason, 0 , inflation_pensions),
         law_pensions = ifelse(responses == not_answered_reason, 0 , law_pensions),
         trust_pensions = ifelse(responses == not_answered_reason, 0 , trust_insurance),
         inappropriate_pensions = ifelse(responses == not_answered_reason, 0 , inappropriate_pensions),
         )%>%
  full_join(y = provincial_totals, by = all_of(level))

pension$reasons = rowSums(pension[, c("knowledge", "finance", "inflation", "law", "trust", "inappropriate")])

pension$reasons_pensions = pension$reasons / (pension$provincial_totals - pension$not_answered_reason)

pension %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

## Mobile Money

- reasons not having a mobile money account

**documentation, finance, trust, bureaucracy**

- faced restrictions in use of mobile money account

```{r echo=FALSE}
mobile_money = data %>%
  select(all_of(level), 
         mobile_money_account, reason_no_mobile_money_account) %>%
  filter(mobile_money_account == "No") %>%
  # filter(My business does not need a mobile money account (because we only/mainly handle cash transactions)) %>%
  mutate(not_answered = ifelse(reason_no_mobile_money_account == "", 1, 0),
         documentation = ifelse(reason_no_mobile_money_account == "Documentation (I do not have one or more of the required documents)", 1, 0),
         finance = ifelse(reason_no_mobile_money_account == "Affordability (The charges are too high)", 1, 0),
         trust = ifelse(reason_no_mobile_money_account == "Insufficient security protocols (I do not feel my money is safe in the mobile money system)", 1, 0),
         bureaucracy = ifelse(reason_no_mobile_money_account == "Bureaucracy (it takes too long to open an account and there are too many processes involved)", 1, 0)
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise(documentation = sum(documentation),
            finance = sum(finance),
            trust = sum(trust),
            bureaucracy = sum(bureaucracy),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(documentation_mobile = documentation / (responses - not_answered_reason),
         finance_mobile = finance / (responses - not_answered_reason),
         trust_mobile = trust / (responses - not_answered_reason),
         bureaucracy_mobile = bureaucracy / (responses - not_answered_reason),
         
         documentation_mobile = ifelse(responses == not_answered_reason, 0 , documentation_mobile),
         finance_mobile = ifelse(responses == not_answered_reason, 0 , finance_mobile),
         trust_mobile = ifelse(responses == not_answered_reason, 0 , trust_mobile),
         bureaucracy_mobile = ifelse(responses == not_answered_reason, 0 , bureaucracy_mobile)
         )%>%
  full_join(y = provincial_totals, by = all_of(level))

mobile_money$reasons = rowSums(mobile_money[, c("documentation", "finance", "trust", "bureaucracy")])

mobile_money$reasons_mobile = mobile_money$reasons / (mobile_money$provincial_totals - mobile_money$not_answered_reason)

mobile_money %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

```{r echo=FALSE}
# restrictions in use of mobile money account
restrictions_mobile_money = data %>% 
  select(all_of(level),
         mobile_money_account, restrictions_use_mobile_money) %>%
  filter(mobile_money_account == "Yes") %>%
  mutate(not_answered = ifelse(restrictions_use_mobile_money == "", 1, 0),
         restrictions_mobile_money_logic = ifelse(restrictions_use_mobile_money == "Yes", 1, 0)) %>%
  group_by(across(all_of(level))) %>%
  summarise(restrictions_mobile_money = sum(restrictions_mobile_money_logic),
            responses = n(),
            not_answered_restrictions_mobile = sum(not_answered)) %>%
  mutate(restrictions_mobile_money_value = restrictions_mobile_money / (responses - not_answered_restrictions_mobile))

restrictions_mobile_money %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

## Investments and Capital Markets

- reasons for not making investments

**knowledge, finance, inflation**

```{r echo=FALSE}
investments = data %>%
  select(all_of(level), 
         investments, reason_no_investments) %>%
  filter(investments == "No") %>%
  # filter(My business does not need a mobile money account (because we only/mainly handle cash transactions)) %>%
  mutate(not_answered = ifelse(reason_no_investments == "", 1, 0),
         knowledge = ifelse(reason_no_investments == "I am not aware of any investment products.", 1, 0),
         finance = ifelse(reason_no_investments == "Inadequate cash flows for investment", 1, 0),
         inflation = ifelse(reason_no_investments == "Inflation", 1, 0),
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise(knowledge = sum(knowledge),
            finance = sum(finance),
            inflation = sum(inflation),
            responses = n(),
            not_answered_reason = sum(not_answered)) %>%
  mutate(knowledge_investments = knowledge / (responses - not_answered_reason),
         finance_investments = finance / (responses - not_answered_reason),
         inflation_investments = inflation / (responses - not_answered_reason),
         
         knowledge_investments = ifelse(responses == not_answered_reason, 0 , knowledge_investments),
         finance_investments = ifelse(responses == not_answered_reason, 0 , finance_investments),
         inflation_investments = ifelse(responses == not_answered_reason, 0 , inflation_investments),
         )%>%
  full_join(y = provincial_totals, by = all_of(level))

investments$reasons = rowSums(investments[, c("knowledge", "finance", "inflation")])

investments$reasons_investments = investments$reasons / (investments$provincial_totals - investments$not_answered_reason)

investments %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

## Combine into 8 measures

- knowledge

- documentation

- legal standing

- finance/ affordability

- inflation

- complicated law/process

- trust

- bureaucracy

- appropriateness

```{r echo=FALSE}
reasons = data %>%
  group_by(across(all_of(level))) %>%
  summarise(n=n()) %>%
  full_join(y = (register %>% select(all_of(level), knowledge_register, finance_register, law_register, bureaucracy_register, reasons_register)), by = all_of(level)) %>%
  full_join((zimra %>% select(all_of(level), knowledge_zimra, finance_zimra, inflation_zimra, law_zimra, bureaucracy_zimra, reasons_zimra)), by = all_of(level)) %>%
  full_join((bank_account %>% select(all_of(level), documentation_account, legal_account, finance_account, trust_account, bureaucracy_account, inappropriate_account, reasons_account)),by = all_of(level)) %>%
  full_join((sme_auction %>% select(all_of(level), knowledge_sme, legal_sme, law_sme, trust_sme, inappropriate_sme, reasons_sme)),by = all_of(level)) %>%
  full_join((commercial_loan %>% select(all_of(level),knowledge_commercial_loan,documentation_commercial_loan,legal_commercial_loan,finance_commercial_loan,inappropriate_commercial_loan, reasons_loan)),by = all_of(level)) %>%
  full_join((business_insurance %>% select(all_of(level), knowledge_insurance,legal_insurance,finance_insurance,inflation_insurance, law_insurance, trust_insurance, inappropriate_insurance, reasons_insurance)),by = all_of(level)) %>%
  full_join((pension %>% select(all_of(level), knowledge_pensions,finance_pensions, inflation_pensions, law_pensions,trust_pensions,inappropriate_pensions, reasons_pensions)),by = all_of(level)) %>%
  full_join((mobile_money %>% select(all_of(level), documentation_mobile,finance_mobile,trust_mobile,bureaucracy_mobile, reasons_mobile)),by = all_of(level)) %>%
  full_join((investments %>% select(all_of(level),knowledge_investments, finance_investments, inflation_investments, reasons_investments)),by = all_of(level))

barrier_reasons = reasons

barrier_reasons$knowledge = rowMeans(reasons[, 
                                      c("knowledge_register", "knowledge_zimra", "knowledge_sme", "knowledge_commercial_loan", "knowledge_insurance", "knowledge_pensions", "knowledge_investments")], na.rm = T)

barrier_reasons$documentation = rowMeans(reasons[, 
                                          c("documentation_account", "documentation_commercial_loan", "documentation_mobile")],  na.rm = T)

barrier_reasons$legal = rowMeans(reasons[, 
                                  c("legal_account", "legal_sme", "legal_commercial_loan", "legal_insurance")],  na.rm = T)

barrier_reasons$finance = rowMeans(reasons[, 
                                    c("finance_register", "finance_zimra", "finance_account", "finance_commercial_loan", "finance_insurance", "finance_pensions", "finance_mobile", "finance_investments")],  na.rm = T)

barrier_reasons$inflation = rowMeans(reasons[,
                                      c("inflation_zimra", "inflation_insurance", "inflation_pensions", "inflation_investments")],  na.rm = T)

barrier_reasons$law = rowMeans(reasons[, 
                                c("law_register", "law_zimra", "law_sme", "law_insurance", "law_pensions")],  na.rm = T)

barrier_reasons$trust = rowMeans(reasons[, 
                                  c("trust_account", "trust_sme", "trust_insurance", "trust_pensions", "trust_mobile")],  na.rm = T)

barrier_reasons$bureaucracy = rowMeans(reasons[, 
                                        c("bureaucracy_register", "bureaucracy_zimra", "bureaucracy_account", "bureaucracy_mobile")],  na.rm = T)

barrier_reasons$inappropriate = rowMeans(reasons[, 
                                          c("inappropriate_account", "inappropriate_sme", "inappropriate_commercial_loan", "inappropriate_insurance", "inappropriate_pensions")],  na.rm = T)

barrier_reasons$reason = rowMeans(barrier_reasons[, c("reasons_register", "reasons_zimra", "reasons_account", "reasons_sme", "reasons_loan", "reasons_insurance", "reasons_pensions", "reasons_mobile", "reasons_investments")], na.rm = T)

```

## Knowledge score

- Very good: 5

- Good: 4

- Average: 3

- Poor: 2

- Very poor: 1

- I don't know anything: 0

```{r echo=FALSE}
# Knowledge score... each out of 5
knowledge_score = data %>%
  select(all_of(level),
         knowledge_banking_services, knowledge_mobile_money_services, knowledge_investements_capital_markets,
         knowledge_business_insurance_products, knowledge_pension_products, knowledge_loans_credit_commercial_banks,
         knowledge_loans_credit_microfinance, knowledge_loans_credit_roscas_isals, knowledge_taxation_regulations) %>%
  mutate(not_answered_banking = ifelse(knowledge_banking_services == "", 1, 0),
         not_answered_mobile = ifelse(knowledge_mobile_money_services == "", 1, 0),
         not_answered_investments = ifelse(knowledge_investements_capital_markets == "", 1, 0),
         not_answered_insurance = ifelse(knowledge_business_insurance_products == "", 1, 0),
         not_answered_pensions = ifelse(knowledge_pension_products == "", 1, 0),
         not_answered_commercial_loan = ifelse(knowledge_loans_credit_commercial_banks == "", 1, 0),
         not_answered_mfi_loan = ifelse(knowledge_loans_credit_microfinance == "", 1, 0),
         not_answered_rosal_loan = ifelse(knowledge_loans_credit_roscas_isals == "", 1, 0),
         not_answered_tax = ifelse(knowledge_taxation_regulations == "", 1, 0),
         
         
         knowledge_banking_services = case_when(
    knowledge_banking_services == "Very good" ~ 5,
    knowledge_banking_services == "Good" ~ 4,
    knowledge_banking_services == "Average" ~ 3,
    knowledge_banking_services == "Poor" ~ 2,
    knowledge_banking_services == "Very poor" ~ 1,
    knowledge_banking_services == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_mobile_money_services = case_when(
    knowledge_mobile_money_services == "Very good" ~ 5,
    knowledge_mobile_money_services == "Good" ~ 4,
    knowledge_mobile_money_services == "Average" ~ 3,
    knowledge_mobile_money_services == "Poor" ~ 2,
    knowledge_mobile_money_services == "Very poor" ~ 1,
    knowledge_mobile_money_services == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_investements_capital_markets = case_when(
    knowledge_investements_capital_markets == "Very good" ~ 5,
    knowledge_investements_capital_markets == "Good" ~ 4,
    knowledge_investements_capital_markets == "Average" ~ 3,
    knowledge_investements_capital_markets == "Poor" ~ 2,
    knowledge_investements_capital_markets == "Very poor" ~ 1,
    knowledge_investements_capital_markets == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_business_insurance_products = case_when(
    knowledge_business_insurance_products == "Very good" ~ 5,
    knowledge_business_insurance_products == "Good" ~ 4,
    knowledge_business_insurance_products == "Average" ~ 3,
    knowledge_business_insurance_products == "Poor" ~ 2,
    knowledge_business_insurance_products == "Very poor" ~ 1,
    knowledge_business_insurance_products == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_pension_products = case_when(
    knowledge_pension_products == "Very good" ~ 5,
    knowledge_pension_products == "Good" ~ 4,
    knowledge_pension_products == "Average" ~ 3,
    knowledge_pension_products == "Poor" ~ 2,
    knowledge_pension_products == "Very poor" ~ 1,
    knowledge_pension_products == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_loans_credit_commercial_banks = case_when(
    knowledge_loans_credit_commercial_banks == "Very good" ~ 5,
    knowledge_loans_credit_commercial_banks == "Good" ~ 4,
    knowledge_loans_credit_commercial_banks == "Average" ~ 3,
    knowledge_loans_credit_commercial_banks == "Poor" ~ 2,
    knowledge_loans_credit_commercial_banks == "Very poor" ~ 1,
    knowledge_loans_credit_commercial_banks == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_loans_credit_microfinance = case_when(
    knowledge_loans_credit_microfinance == "Very good" ~ 5,
    knowledge_loans_credit_microfinance == "Good" ~ 4,
    knowledge_loans_credit_microfinance == "Average" ~ 3,
    knowledge_loans_credit_microfinance == "Poor" ~ 2,
    knowledge_loans_credit_microfinance == "Very poor" ~ 1,
    knowledge_loans_credit_microfinance == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_loans_credit_roscas_isals = case_when(
    knowledge_loans_credit_roscas_isals == "Very good" ~ 5,
    knowledge_loans_credit_roscas_isals == "Good" ~ 4,
    knowledge_loans_credit_roscas_isals == "Average" ~ 3,
    knowledge_loans_credit_roscas_isals == "Poor" ~ 2,
    knowledge_loans_credit_roscas_isals == "Very poor" ~ 1,
    knowledge_loans_credit_roscas_isals == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  ),
  knowledge_taxation_regulations = case_when(
    knowledge_taxation_regulations == "Very good" ~ 5,
    knowledge_taxation_regulations == "Good" ~ 4,
    knowledge_taxation_regulations == "Average" ~ 3,
    knowledge_taxation_regulations == "Poor" ~ 2,
    knowledge_taxation_regulations == "Very poor" ~ 1,
    knowledge_taxation_regulations == "I don’t know anything" ~ 0,
    TRUE ~ as.double(-1)
  )
  ) %>%
  group_by(across(all_of(level))) %>%
  summarise_if(is.numeric, sum) %>%
  full_join(y = provincial_totals, by = all_of(level))

knowledge_score$not_answered = rowSums(knowledge_score[, c("not_answered_banking", "not_answered_mobile", "not_answered_investments",
                                                           "not_answered_insurance", "not_answered_pensions", "not_answered_commercial_loan",
                                                           "not_answered_mfi_loan", "not_answered_rosal_loan", "not_answered_tax")])

knowledge_score$score = rowSums(knowledge_score[, c("knowledge_banking_services", "knowledge_mobile_money_services", "knowledge_investements_capital_markets",
         "knowledge_business_insurance_products", "knowledge_pension_products", "knowledge_loans_credit_commercial_banks",
         "knowledge_loans_credit_microfinance", "knowledge_loans_credit_roscas_isals", "knowledge_taxation_regulations")])

knowledge_score_final = knowledge_score %>%
  mutate(max_score = (5* (provincial_totals - not_answered)) * 9,
         score_value = score / max_score
         )

knowledge_score_final %>%
  bind_rows(summarise_all(., ~if(is.numeric(.)) sum(.) else "total")) %>%
  kable() %>%
  kable_styling()
```

```{r}
barriers_critera = data %>%
  group_by(across(all_of(level))) %>%
  summarise(n=n()) %>%
  full_join(y = (barrier_reasons %>% select(all_of(level), knowledge, documentation, legal, finance, inflation, law, trust, bureaucracy, inappropriate, reason)), 
            by = all_of(level)) %>%
  full_join(y = (knowledge_score_final %>% select(all_of(level), score_value))) %>%
  full_join(y = (restrictions_bank_account %>% select(all_of(level), restrictions_bank_account_value))) %>%
  full_join(y = (restrictions_mobile_money %>% select(all_of(level), restrictions_mobile_money_value))) %>%
  select(all_of(level), n, all_of(criteria)) %>%
  mutate_all(~replace(.,is.na(.), 0))

barriers_critera$barriers_score = rowSums(barriers_critera[, c(
  all_of(criteria))])

barriers_critera$barriers_normalise = (barriers_critera$barriers_score / ncriteria)

barriers_critera$barriers_percentage = round((barriers_critera$barriers_normalise * 100), 2)
  
barriers_critera %>%
  kable() %>%
  kable_styling()
```


```{r}
write.csv(barriers_critera, file = "~/SIVIOgit/barriers_criteria.csv")
```